### 2021-04-08 docs/paper/main.tex
Adding to examples

\documentclass[nofootinbib,superscriptaddress,a4paper,twocolumn,longbibliography,floatfix,pra]{revtex4-2}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

\usepackage{enumitem}

\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{physics}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage[left=23mm,right=13mm,top=35mm,columnsep=15pt]{geometry} 
\usepackage{adjustbox}
\usepackage{placeins}
\usepackage[T1]{fontenc}
\usepackage{lipsum}
\usepackage{csquotes}

\usepackage{listings}
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{tqblue}{HTML}{08293d}
\definecolor{backcolour}{HTML}{fefdf5}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize\color{tqblue},
    breakatwhitespace=false,         
    breaklines=true,
    postbreak=\mbox{\textcolor{magenta}{$\hookrightarrow$}\space},                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\usepackage{booktabs}
\usepackage{soul}

\usepackage{xspace}
\newcommand{\expect}[2]{\ensuremath{\langle #1 \rangle_{#2}}}

\setlength{\parindent}{0cm}

\usepackage[pdftex, pdftitle={Article}, pdfauthor={Author}]{hyperref} % For hyperlinks in the PDF
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

%-----------------------------------------------------------------------------%
% Macros:
%-----------------------------------------------------------------------------%

\newcommand{\comment}[1]{\begin{quote}\sf 
    \textcolor{blue}{[#1]}\end{quote}}
\newcommand{\linecomment}[1]{\textcolor{blue}{\sf[#1]}}

\newcommand{\tinyspace}{\mspace{1mu}}
\newcommand{\microspace}{\mspace{0.5mu}}
\newcommand{\negsmallspace}{\mspace{-1.5mu}}
\newcommand{\pt}{\operatorname{T}}
\newcommand{\ppt}{\operatorname{PPT}}
\newcommand{\sep}{\operatorname{Sep}}
\renewcommand{\int}{\operatorname{int}}
\renewcommand{\det}{\operatorname{Det}}
\renewcommand{\vec}{\operatorname{vec}}
\newcommand{\fid}{\operatorname{F}}
\newcommand{\im}{\operatorname{im}}

\renewcommand{\tr}{\operatorname{Tr}}
\renewcommand{\t}{{\scriptscriptstyle\mathsf{T}}}

\renewcommand{\abs}[1]{\lvert #1 \rvert}
\newcommand{\bigabs}[1]{\bigl\lvert #1 \bigr\rvert}
\newcommand{\Bigabs}[1]{\Bigl\lvert #1 \Bigr\rvert}
\newcommand{\biggabs}[1]{\biggl\lvert #1 \biggr\rvert}
\newcommand{\Biggabs}[1]{\Biggl\lvert #1 \Biggr\rvert}

\renewcommand{\ip}[2]{\langle #1 , #2\rangle}
\newcommand{\bigip}[2]{\bigl\langle #1, #2 \bigr\rangle}
\newcommand{\Bigip}[2]{\Bigl\langle #1, #2 \Bigr\rangle}
\newcommand{\biggip}[2]{\biggl\langle #1, #2 \biggr\rangle}
\newcommand{\Biggip}[2]{\Biggl\langle #1, #2 \Biggr\rangle}

\newcommand{\ceil}[1]{\lceil #1 \rceil}
\newcommand{\bigceil}[1]{\bigl\lceil #1 \bigr\rceil}
\newcommand{\Bigceil}[1]{\Bigl\lceil #1 \Bigr\rceil}
\newcommand{\biggceil}[1]{\biggl\lceil #1 \biggr\rceil}
\newcommand{\Biggceil}[1]{\Biggl\lceil #1 \Biggr\rceil}

\newcommand{\floor}[1]{\lfloor #1 \rfloor}
\newcommand{\bigfloor}[1]{\bigl\lfloor #1 \bigr\rfloor}
\newcommand{\Bigfloor}[1]{\Bigl\lfloor #1 \Bigr\rfloor}
\newcommand{\biggfloor}[1]{\biggl\lfloor #1 \biggr\rfloor}
\newcommand{\Biggfloor}[1]{\Biggl\lfloor #1 \Biggr\rfloor}

\newcommand{\bignorm}[1]{\bigl\lVert\tinyspace #1 \tinyspace\bigr\rVert}
\newcommand{\Bignorm}[1]{\Bigl\lVert\tinyspace #1 \tinyspace\Bigr\rVert}
\newcommand{\biggnorm}[1]{\biggl\lVert\tinyspace #1 \tinyspace\biggr\rVert}
\newcommand{\Biggnorm}[1]{\Biggl\lVert\tinyspace #1 \tinyspace\Biggr\rVert}

\newcommand{\bigtriplenorm}[1]{
  \bigl\lvert\!\microspace\bigl\lvert\!\microspace\bigl\lvert #1 
  \bigr\rvert\!\microspace\bigr\rvert\!\microspace\bigr\rvert}

\newcommand{\Bigtriplenorm}[1]{
  \Bigl\lvert\!\microspace\Bigl\lvert\!\microspace\Bigl\lvert #1 
  \Bigr\rvert\!\microspace\Bigr\rvert\!\microspace\Bigr\rvert}

\newcommand{\biggtriplenorm}[1]{
  \biggl\lvert\!\microspace\biggl\lvert\!\microspace\biggl\lvert #1 
  \biggr\rvert\!\microspace\biggr\rvert\!\microspace\biggr\rvert}

\newcommand{\Biggtriplenorm}[1]{
  \Biggl\lvert\!\microspace\Biggl\lvert\!\microspace\Biggl\lvert #1 
  \Biggr\rvert\!\microspace\Biggr\rvert\!\microspace\Biggr\rvert}

\newcommand{\triplenorm}[1]{
  \left\lvert\!\microspace\left\lvert\!\microspace\left\lvert #1 
  \right\rvert\!\microspace\right\rvert\!\microspace\right\rvert}
\def\iso{\cong}
\newcommand{\defeq}{\triangleq}

\newcommand{\bigket}[1]{
  \bigl\lvert\microspace #1 \microspace \bigr\rangle}

\newcommand{\Bigket}[1]{
  \Bigl\lvert\microspace #1 \microspace \Bigr\rangle}

\newcommand{\biggket}[1]{
  \biggl\lvert\microspace #1 \microspace \biggr\rangle}

\newcommand{\Biggket}[1]{
  \Biggl\lvert\microspace #1 \microspace \Biggr\rangle}

\newcommand{\bigbra}[1]{
  \bigl\langle\microspace #1 \microspace \bigr\rvert}

\newcommand{\Bigbra}[1]{
  \Bigl\langle\microspace #1 \microspace \Bigr\rvert}

\newcommand{\biggbra}[1]{
  \biggl\langle\microspace #1 \microspace \biggr\rvert}

\newcommand{\Biggbra}[1]{
  \Biggl\langle\microspace #1 \microspace \Biggr\rvert}

\newcommand{\I}{\mathbb{I}}

\newcommand{\setft}[1]{\mathrm{#1}}
\newcommand{\Density}{\setft{D}}
\newcommand{\Pos}{\setft{Pos}}
\newcommand{\Unitary}{\setft{U}}
\newcommand{\Herm}{\setft{Herm}}
\newcommand{\Lin}{\setft{L}}

\newcommand{\complex}{\mathbb{C}}
\renewcommand{\natural}{\mathbb{N}}
\newcommand{\integer}{\mathbb{Z}}

\usepackage{FiraSans}
\newcommand{\poly}{\mathit{poly}}
\newcommand{\toqitofont}{%
	\fontfamily{FiraSans}%
	\selectfont}

\newcommand{\toqito}{ $|${\toqitofont toqito}$\rangle$\xspace}
\newcommand{\numpy}{\texttt{numpy}\xspace}
\newcommand{\tequila}{\textsc{toqito}}
\newenvironment{mylist}[1]{\begin{list}{}{
	\setlength{\leftmargin}{#1}
	\setlength{\rightmargin}{0mm}
	\setlength{\labelsep}{2mm}
	\setlength{\labelwidth}{8mm}
	\setlength{\itemsep}{0mm}}}
	{\end{list}}

\newenvironment{namedtheorem}[1]
	       {\begin{trivlist}\item {\bf #1.}\em}{\end{trivlist}}

\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}
\newcommand{\Z}{\mathcal{Z}}
\newcommand{\W}{\mathcal{W}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Q}{\mathcal{Q}}
\renewcommand{\P}{\mathcal{P}}
\renewcommand{\S}{\mathcal{S}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\K}{\mathcal{K}}
\renewcommand{\L}{\mathcal{L}}

\newcommand{\yes}{\text{yes}}
\newcommand{\no}{\text{no}}

\newcommand{\class}[1]{\textup{#1}}
\newcommand{\reg}[1]{\textsf{#1}}

\def\BB84{\mathsf{BB84}}
\def\CHSH{\mathsf{CHSH}}
\def\MUB{\mathsf{MUB}}

\begin{document}
\title{\toqito: Theory of quantum information toolkit}

\author{Vincent Russo}
\email[E-mail:]{vincentrusso1@gmail.com}
\affiliation{-}

\date{\today}

\begin{abstract}
    \toqito is an open source Python library for studying various objects in
    quantum information, namely, states, channels, and measurements. \toqito
    focuses on providing numerical tools to study problems pertaining to
    entanglement theory, nonlocal games, and other aspects of quantum
    information that are often associated with computer science. We illustrate
    some of the core features of \toqito and show how it can be applied to
    certain problems in quantum information. Using \toqito, we provide an
    answer to one of the problems left open in~\cite{johnston2016extended} by
    showing a more minimal example of an extended nonlocal game that possesses
    a quantum advantage. We also make use of \toqito to numerically verify a
    number of known results in the literature on subjects including quantum
    state discrimination and nonlocal games. We hope that these numerical tools
    can be used to aid researchers in further investigating these areas as well
    as students studying quantum information.
\end{abstract}

\maketitle

%-----------------------------------------------------------------------------%
\section{Introduction}
\label{sec:introduction}
%-----------------------------------------------------------------------------%

\comment{Intro}

While there are many software packages that exist in the quantum software
ecosystem, few of them have a core focus on quantum information.  Packages such
as XX and XX specialize in quantum circuit synthesis and packages XX, XX, and
XX center on problems pertaining to quantum machine learning~\cite{}. Software
packages with a focus on quantum information .... For a more thorough survey on
software packages pertaining to quantum information, consult the following
survey~\cite{}.

\toqito is an ... Documentation and tutorials are available on the \toqito
\href{https://github.com/vprusso/toqito}{GitHub repository}~\cite{toqito}.

%-----------------------------------------------------------------------------%
\section{Fundamental objects}
\label{sec:fundemental_objects}
%-----------------------------------------------------------------------------%

Arguably, the core building blocks of quantum information consist of
\emph{states}, \emph{channels}, and \emph{measurements}.\\

\subsection{States}\label{sec:states}

A \emph{quantum state} is a density operator
\begin{equation}
    \rho \in \Density(\X)
\end{equation}
where $\X$ is a complex Euclidean space and where $\Density(\cdot)$ represents
the set of density matrices, that is, the set of matrices that are positive
semidefinite with trace equal to $1$.

%-----------------------------------------------------------------------------%
\subsubsection{Quantum states}
\label{sec:quantum_states}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsubsection{Properties of quantum states}
\label{sec:properties_of_quantum_states}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsubsection{Distance metrics for quantum states}
\label{sec:distance_metrics_for_quantum_states}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsection{Channels}
\label{sec:channels}
%-----------------------------------------------------------------------------%

A \emph{quantum channel} can be defined as a completely positive and trace
preserving linear map.
\\

More formally, let $\X$ and $\Y$ represent complex Euclidean spaces and let
$\Lin(\cdot)$ represent the set of linear operators. Then a quantum channel,
$\Phi$ is defined as
\begin{equation}
    \Phi: \Lin(\X) \rightarrow \Lin(\Y)
\end{equation}
such that $\Phi$ is completely positive and trace preserving.

%-----------------------------------------------------------------------------%
\subsubsection{Quantum channels}
\label{sec:quantum_channels}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsubsection{Properties of quantum states}
\label{sec:properties_of_quantum_states}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsubsection{Operations on quantum states}
\label{sec:operations_on_quantum_states}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsection{Measurements}
\label{sec:measurements}
%-----------------------------------------------------------------------------%

A \emph{measurement} can be defined as a function
\begin{equation}
    \mu: \Sigma \rightarrow \Pos(\X)
\end{equation}
satisfying
\begin{equation}
    \sum_{a \in \Sigma} \mu(a) = \I_{\X}
\end{equation}
where $\Sigma$ represents a set of measurement outcomes and where $\mu(a)$
represents the measurement operator associated with outcome $a \in \Sigma$.

%-----------------------------------------------------------------------------%
\section{Examples and Applications}
\label{sec:examples_and_applications}
%-----------------------------------------------------------------------------%

The \toqito software package \comment{TODO: elaborate}

%-----------------------------------------------------------------------------%
\subsection{Nonlocal games}\label{sec:nonlocal_games}
%-----------------------------------------------------------------------------%

In this section, we are going to cover the notion of a \emph{nonlocal game}; a
mathematical framework that abstractly models a physical system. The simplest
instance of a nonlocal game involves two players--Alice and Bob, who are not
allowed to communicate with each other once the game has started and who play
cooperatively against an adversary referred to as the referee. \\

A primary challenge that arises when studying these games is to determine the
maximum probability with which Alice and Bob are able to achieve a winning
outcome. \\

The probability is dependent on the type of \emph{strategy} that Alice and Bob
use in the game. A \emph{classical strategy} is one in which Alice and Bob have
access to classical resources and play deterministically. The best that Alice
and Bob can do using a classical strategy is known as the \emph{classical
value} of the game.  Similarly, a \emph{quantum strategy} is one in which Alice
and Bob have access to quantum resources in the form of a shared quantum state
and respective sets of measurements. The best that Alice and Bob can do using a
quantum strategy is known as the \emph{quantum value} of the game.
\\

\begin{figure}[!htpb]
    \centering
    \includegraphics[width=0.4\textwidth]{pics/nonlocal_game_quantum_strategy.pdf}
    \caption{A nonlocal game}
    \label{fig:nonlocal_game}
\end{figure}

More formally, a nonlocal game, $G$, is specified as a pair $(\pi, V)$ where
$\pi$ is a probability distribution
\begin{equation}
    \pi : \Sigma_A \times \Sigma_B \rightarrow [0,1]
\end{equation}
on the Cartesian product of two alphabets $\Sigma_A$ and $\Sigma_B$, and $V$ is
a function
\begin{equation}
    V : \Gamma_A \times \Gamma_B \times \Sigma_A \times \Sigma_B \rightarrow [0,1].
\end{equation}
We shall represent
\begin{equation}
    \Sigma = \Sigma_A \times \Sigma_B 
    \ \ \text{and} \ \ 
    \Gamma = \Gamma_A \times \Gamma_B
\end{equation}
to denote the respective sets of questions and answers for Alice and Bob.

%-----------------------------------------------------------------------------%
\subsubsection{Classical strategies for nonlocal games}
\label{sec:classical_strategies_for_nonlocal_games}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsubsection{Quantum strategies for nonlocal games}
\label{sec:quantum_strategies_for_nonlocal_games}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsubsection{Non-signaling strategies for nonlocal games}
\label{sec:non_signaling_strategies_for_nonlocal_games}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsubsection{Parallel repetition for nonlocal games}
\label{sec:parallel_repeptitionfor_nonlocal_games}
%-----------------------------------------------------------------------------%

A game $G$ has the property of \emph{strong parallel repetition} if the value
of the game raised to the power $r$ is equal to the value of running the game
$r$ times.

%-----------------------------------------------------------------------------%
\subsection{XOR nonlocal games}
\label{sec:xor_nonlocal_games}
%-----------------------------------------------------------------------------%

A \emph{two-player XOR nonlocal game} is a nonlocal game in which the winning
condition is predicated on an XOR function~\cite{cleve2004consequences}.

%-----------------------------------------------------------------------------%
\subsubsection{Example: The CHSH game}
\label{sec:chsh_game}
%-----------------------------------------------------------------------------%

The \emph{CHSH game} is a two-player XOR game with the following probability
distribution 
\begin{equation}
    \pi(x,y) = \frac{1}{4},
\end{equation}
and question and answer sets
\begin{equation}
    \begin{aligned}
        (x,y) \in \Sigma_A \times \Sigma_B \quad \text{and} \quad (a,b) \in
        \Gamma_A \times \Gamma_B,
    \end{aligned}
\end{equation}
where 
\begin{equation}
    \Sigma_A = \Sigma_B = \Gamma_A = \Gamma_B = \{0,1\}.
\end{equation}
Alice and Bob win the CHSH game if and only if the following equation is
satisfied
\begin{equation}
    a \oplus b = x \land y.
\end{equation}
For each question scenario, Table~\ref{tab:chsh_winning} provides what the
winning condition must be equal to for each question tuple to induce a winning
outcome.
\begin{table}[!htpb]\label{tab:chsh_winning}
    \begin{tabular}{|c|c|c|}
        \hline
        \textbf{$x$} & \textbf{$y$} & \textbf{$a \oplus b$} \\ \hline
        0 & 0 & 0 \\ \hline
        0 & 1 & 0 \\ \hline
        1 & 0 & 0 \\ \hline
        1 & 1 & 1 \\ \hline
    \end{tabular}
    \caption{Question pairs and respective winning outcomes for the CHSH game.}
\end{table}
In order to specify an XOR nonlocal game in \toqito, we will define two
matrices:

\begin{itemize}[noitemsep]
    \item \texttt{prob\_mat}: A matrix whose $(x,y)^{th}$-entry corresponds to
        the probability that Alice receives question $x$ and Bob receives
        question $y$. \\
    \item \texttt{pred\_mat}: A matrix whose $(x,y)^{th}$-entry corresponds to
        the winning choice of $a$ and $b$ when Alice receives $x$ and Bob
        receives $y$ from the referee.
\end{itemize}

We can encode the CHSH game, $G_{\CHSH} = (\pi, V)$, in \toqito by defining the
\texttt{prob\_mat} and \texttt{pred\_mat} variables as is shown in
Figure~\ref{fig:chsh}.

\begin{figure}[!htpb]
    \centering
    \lstinputlisting[language=Python]{code/chsh.py}        
    \caption{Define the CHSH XOR nonlocal game.}
    \label{fig:chsh}
\end{figure}

That is, the \texttt{prob\_mat} variable encapsulates that each question pair
$\{(0,0),(0,1),(1,0),(1,1)\}$ is equally likely. The \texttt{pred\_mat}
variable indicates what the winning outcome of Alice and Bob should be. For
instance, \texttt{pred\_mat[0][0] = 0} describes the scenario where Alice and
Bob both receive $0$ as input. As we want to satisfy the winning condition $a
\oplus b = x \land y$, we must have that $a \oplus b = 0$ to satisfy the case
when both $x$ and $y$ are equal to zero. A similar logic can be followed to
populate the remaining entries of the \texttt{pred\_mat} variable.

What is very intriguing about the CHSH game is that it is an example of a
nonlocal game where the players can do \emph{strictly} better if they make use
of a quantum strategy instead of a classical one. It is known that the best
that Alice and Bob can do when using a classical strategy is to win $G_{\CHSH}$
with probability $3/4$, however, there exists a quantum strategy that enables
Alice and Bob to win with a strictly higher probability of $\cos^2(\pi/8)
\approx 0.8536$~\cite{cleve2004consequences}. We can numerically verify this
fact in \toqito as is shown in Figure~\ref{fig:chsh_classical_quantum}

\begin{figure}[!htpb]
    \centering
    \lstinputlisting[language=Python]{code/chsh_classical_quantum.py}        
    \caption{Calculate the classical and quantum value of the CHSH XOR nonlocal
    game.}
    \label{fig:chsh_classical_quantum}
\end{figure}

Using \toqito, we can also compute how a given XOR nonlocal game behaves under
parallel repetition. It holds from~\cite{cleve2008perfect} that the quantum
value of any XOR nonlocal game obeys strong parallel repetition. That is, it
holds that

\begin{equation}
    \omega^*(G^n) = \omega^*(G)^n 
\end{equation}

for any XOR nonlocal game, $G$. The \texttt{XORGame} class takes an optional
argument, \texttt{reps}, that specifies how many parallel repetitions to run
the game for (by default, this argument is equal to one). For instance, taking
the \texttt{prob\_mat} and \texttt{pred\_mat} variables defined in
Figure~\ref{fig:chsh} that characterize $G_{\CHSH}$, we can consider the value
of the $r$-fold parallel repetition of $G_{\CHSH}$.
Figure~\ref{fig:chsh_parallel_repetition} illustrates how one may compute the
$2$-fold and $3$-fold parallel repetition of the CHSH game for the quantum
value.

\begin{figure}[!htpb]
    \centering
    \lstinputlisting[language=Python]{code/chsh_parallel_repetition.py}        
    \caption{Calculate $2$-fold and $3$-fold parallel repetition of the CHSH game.}
    \label{fig:chsh_parallel_repetition}
\end{figure}

%-----------------------------------------------------------------------------%
\subsection{Extended nonlocal games}
\label{sec:extended_nonlocal_games}
%-----------------------------------------------------------------------------%

In this section we shall define the concept of an \emph{extended nonlocal
game}. Extended nonlocal games are a more general abstraction of nonlocal games
wherein the referee, who previously only provided questions and answers to the
players, now shares a state with the players and is able to perform a
measurement on that shared state.
\\

Every extended nonlocal game has a \emph{value} associated to it. Analogously
to nonlocal games, this value is a quantity that dictates how well the players
can perform a task in the extended nonlocal game model when given access to
certain resources. We will be using \toqito to calculate these quantities.
\\

Extended nonlocal games have a natural physical interpretation in the setting
of tripartite steering~\cite{cavalcanti2015detection} and in device-independent
quantum scenarios~\cite{tomamichel2013monogamy}, For more information on
extended nonlocal games, please refer to~\cite{johnston2016extended,
russo2017extended, russo2017thesis}.

%-----------------------------------------------------------------------------%
\subsubsection{The extended nonlocal game model}
\label{sec:extended_nonlocal_game_model}
%-----------------------------------------------------------------------------%

An extended nonlocal game is similar to a nonlocal game in the sense that it is
a cooperative game played between two players Alice and Bob against a referee.
The game begins much like a nonlocal game, with the referee selecting and
sending a pair of questions $(x,y)$ according to a fixed probability
distribution. Once Alice and Bob receive $x$ and $y$, they respond with
respective answers $a$ and $b$. Unlike a nonlocal game, the outcome of an
extended nonlocal game is determined by measurements performed by the referee
on its share of the state initially provided to it by Alice and Bob.

\begin{figure}[!htpb]
    \centering
    \includegraphics[width=0.4\textwidth]{pics/extended_nonlocal_game.pdf}
    \caption{An extended nonlocal game}
    \label{fig:extended_nonlocal_game}
\end{figure}

Specifically, Alice and Bob's winning probability is determined by collections
of measurements, $V(a,b|x,y) \in \Pos(\R)$, where $\R = \complex^m$ is a
complex Euclidean space with $m$ denoting the dimension of the referee's
quantum system--so if Alice and bob's response $(a,b)$ to the question pair
$(x,y)$ leaves the referee's system in the quantum state
\begin{equation}
    \sigma_{a,b}^{x,y} \in \Density(\R),
\end{equation}
then their winning and losing probabilities are given by
\begin{equation}
    \ip{V(a,b|x,y)}{\sigma_{a,b}^{x,y}} \quad \text{and} \quad \ip{\I -
    V(a,b|x,y)}{\sigma_{a,b}^{x,y}}.
\end{equation}

%-----------------------------------------------------------------------------%
\subsubsection{Strategies for extended nonlocal games}
\label{sec:strategies_for_extended_nonlocal_games}
%-----------------------------------------------------------------------------%

An extended nonlocal game $G$ is defined by a pair $(\pi, V)$, where $\pi$ is a
probability distribution of the form
\begin{equation}
    \pi: \Sigma_A \times \Sigma_B \rightarrow \left[0, 1\right]
\end{equation}
on the Cartesian product of two alphabets $\Sigma_A$ and $\Sigma_B$, and $V$ is
a function of the form
\begin{equation}
    V: \Gamma_A \times \Gamma_B \times \Sigma_A \times \Sigma_B \rightarrow
    \Pos(\R)
\end{equation}
for $\Sigma_A$ and $\Sigma_B$ as above, $\Gamma_A$ and $\Gamma_B$ being
alphabets, and $\R$ refers to the referee's space. Just as in the case for
nonlocal games, we shall use the convention that
\begin{equation}
    \Sigma = \Sigma_A \times \Sigma_B \quad \text{and} \quad \Gamma = \Gamma_A
    \times \Gamma_B
\end{equation}
to denote the respective sets of questions asked to Alice and Bob and the sets
of answers sent from Alice and Bob to the referee.

When analyzing a strategy for Alice and Bob, it may be convenient to define a
function
\begin{equation}
    K: \Gamma_A \times \Gamma_B \times \Sigma_A \times \Sigma_B \rightarrow
    \Pos(\R).
\end{equation}
We can represent Alice and Bob's winning probability for an extended nonlocal game as
\begin{equation}
    \sum_{(x,y) \in \Sigma} \pi(x,y) \sum_{(a,b) \in \Gamma}
    \ip{V(a,b|x,y)}{K(a,b|x,y)}.
\end{equation}

%-----------------------------------------------------------------------------%
\subsubsection{The BB84 extended nonlocal game}
%-----------------------------------------------------------------------------%

The \emph{BB84 extended nonlocal game} is defined as follows. Let $\Sigma_A =
\Sigma_B = \Gamma_A = \Gamma_B = \{0,1\}$, define
\begin{equation}
    \begin{aligned}
        V(0,0|0,0) = 
        \begin{pmatrix} 1 & 0 \\ 0 & 0 \end{pmatrix}, &\quad
        V(0,0|1,1) = 
        \frac{1}{2} \begin{pmatrix} 1 & 1 \\ 1 & 1 \end{pmatrix}, \\
        V(1,1|0,0) = 
        \begin{pmatrix} 0 & 0 \\ 0 & 1 \end{pmatrix}, &\quad
        V(1,1|1,1) = 
        \frac{1}{2} \begin{pmatrix} 1 & -1 \\ -1 & 1\end{pmatrix}
    \end{aligned}
\end{equation}
define
\begin{equation}
    V(a,b|x,y) = \begin{pmatrix} 0 & 0 \\ 0 & 0 \end{pmatrix}
\end{equation}
for all $a \not= b$ or $x \not= y$, define $\pi(0, 0) = \pi(1, 1) =
\frac{1}{2}$, and define $\pi(x,y) = 0$ if $x \not= y$.

We can encode the BB84 extended nonlocal game, $G_{\BB84} = (\pi, V)$, in
\numpy arrays where \texttt{prob\_mat} corresponds to the probability
distribution $\pi$ and where \texttt{pred\_mat} corresponds to the operator
$V$.

\begin{figure}[!htpb]
    \centering
    \lstinputlisting[language=Python]{code/bb84_game.py}        
    \caption{Define the BB84 extended nonlocal game.}
    \label{fig:bb84_game}
\end{figure}

In the following sections, we will use the BB84 extended nonlocal game as an
example for how one can define and compute the values of an extended nonlocal
game in \toqito.

%-----------------------------------------------------------------------------%
\subsubsection{Standard quantum strategies for extended nonlocal games}
\label{sec:standard_quantum_strategies_for_extended_nonlocal_games}
%-----------------------------------------------------------------------------%

A \emph{standard quantum strategy} for an extended nonlocal game consists of
finite-dimensional complex Euclidean spaces $\U$ for Alice and $\V$ for Bob, a
quantum state $\sigma \in \Density(\U \otimes \R \otimes \V)$ and two
collections of measurements
\begin{equation*}
    \{A_a^x : a \in \Gamma_A\} \subset \Pos(\U)
    \ \ \text{and} \ \
    \{B_b^y : b \in \Gamma_B\} \subset \Pos(\V),
\end{equation*}
for each $x \in \Sigma_A$ and $y \in \Sigma_B$. The winning probability for
such a strategy in this game $G = (\pi, V)$ is given by
\begin{equation}
    \sum_{(x,y) \in \Sigma} \pi(x,y) \sum_{(a,b) \in \Gamma} \ip{A_a^x \otimes
    V(a,b|x,y) \otimes B_b^y}{\sigma}
\end{equation}
For a given extended nonlocal game $G = (\pi, V)$, we write $\omega^*(G)$ to
denote the \emph{standard quantum value} of $G$, which is the supremum value of
Alice and Bob's winning probability over all standard quantum strategies.

In~\cite{tomamichel2013monogamy}, it was shown that
\begin{equation}
    \omega^*(G_{\BB84}) = \cos^2(\pi/8) \approx 0.8536.
\end{equation}
We can verify this fact using \toqito in the following manner.
\begin{figure}[!htpb]
    \centering
    \lstinputlisting[language=Python]{code/bb84_game_quantum.py}        
    \caption{Calculate the standard quantum value of the BB84 extended nonlocal
    game.}
    \label{fig:bb84_game_quantum}
\end{figure}

\comment{note on calculating quantum values like nlg}

%-----------------------------------------------------------------------------%
\subsubsection{Unentangled strategies for extended nonlocal games}
\label{sec:unentangled_strategies_for_extended_nonlocal_games}
%-----------------------------------------------------------------------------%

An \emph{unentangled strategy} for an extended nonlocal game is simply a
standard quantum strategy for which the state $\sigma \in \Density(\U \otimes
\R \otimes \V)$ initially prepared by Alice and Bob is fully separable.
\\

For a given extended nonlocal game $G = (\pi, V)$, we write $\omega(G)$ to
denote the \emph{unentangled value} of $G$, which is the supremum value for
Alice and Bob's winning probability in $G$ over all unentangled strategies. The
unentangled value of any extended nonlocal game, $G$, may be written as
\begin{equation}
    \omega(G) = \max_{f,g} \Bignorm{\sum_{(x,y) \in \Sigma} \pi(x,y) V(f(x),
    g(y)|x,y)}
\end{equation}
where the maximum is over all functions $f : \Sigma_A \rightarrow \Gamma_A$ and
$g : \Sigma_B \rightarrow \Gamma_B$.
\\

As we did with the standard quantum value in
Section~\ref{sec:standard_quantum_strategies_for_extended_nonlocal_games}, we
can similarly compute the unentangled value of $G_{\BB84}$:
\begin{figure}[!htpb]
    \centering
    \lstinputlisting[language=Python]{code/bb84_game_unentangled.py}        
    \caption{Calculate the standard quantum value of the BB84 extended nonlocal
    game.}
    \label{fig:bb84_game_unentangled}
\end{figure}
This agrees with what was shown in~\cite{tomamichel2013monogamy}
and~\cite{johnston2016extended} that
\begin{equation}
    \omega(G_{\BB84}) = \cos^2(\pi/8) \approx 0.8536.
\end{equation}
Both the unentangled and standard quantum values for $G_{\BB84}$ are equal. In
general though, there do exist extended nonlocal games where the quantum value
is strictly higher than the unentangled value. Such an extended nonlocal where
the referee's measurements are based on mutually unbiased bases was found
in~\cite{johnston2016extended}.

Recall that two orthonormal bases
\begin{equation*}
    \B_0 = \{u_a : a \in \Sigma\} \subset \complex^{\Sigma} \ \ 
    \text{and} \ \
    \B_1 = \{v_a : a \in \Sigma\} \subset \complex^{\Sigma}
\end{equation*}
are \emph{mutually unbiased} if and only if $\abs{\ip{u_a}{v_b}} =
1/\sqrt{\Sigma}$ for all $a, b \in \Sigma$.  For $n \in \natural$, a set of
orthonormal bases $\{\B_0, \ldots, \B_{n-1}\}$ are \emph{mutually unbiased
bases} if and only if every basis is mutually unbiased with every other basis
in the set, that is, $\B_x$ is mutually unbiased with $\B_{x^{\prime}}$ for all
$x \not= x^{\prime}$ with $x, x^{\prime} \in \Sigma$.

Let $G_{\MUB}^{\abs{\Sigma}, \abs{\Gamma}} = (\pi, V)$ represent the
\emph{MUB$_{\abs{\Sigma}, \abs{\Gamma}}$ extended nonlocal game} where the
measurement operators possessed by the referee are defined in terms of
$\abs{\Sigma}$ mutually unbiased bases--each of dimension $\abs{\Gamma}$.

As an example, consider $G_{\MUB}^{4, 3}$. Let $\Sigma_A =
\Sigma_B = \{0, 1, 2, 3\}$ and $\Gamma_A = \Gamma_B = \{0, 1, 2\}$, let $\zeta
= \exp(\frac{2\pi i}{3})$ and consider the following four mutually unbiased
bases:
\begin{equation}
    \begin{aligned}
        \B_0 &= \{e_0, e_1, e_2\}, \\
        \B_1 &= \{\frac{e_0 + e_1 + e_2}{\sqrt{3}}, 
                  \frac{e_0 + \zeta^2 e_1 + \zeta e_2}{\sqrt{3}}, 
                  \frac{e_0 + \zeta e_1 + \zeta^2 e_2}{\sqrt{3}}\}, \\
        \B_2 &= \{\frac{e_0 + e_1 + \zeta e_2}{\sqrt{3}},
                  \frac{e_0 + \zeta^2 e_1 + \zeta^2e_2}{\sqrt{3}},
                  \frac{e_0 + \zeta e_1 + e_2}{\sqrt{3}}\}, \\
        \B_3 &= \{\frac{e_0 + e_1 + \zeta^2 e_2}{\sqrt{3}},
                  \frac{e_0 + \zeta^2 e_1 + e_2}{\sqrt{3}},
                  \frac{e_0 + \zeta e_1 + \zeta e_2}{\sqrt{3}}\}.
    \end{aligned}
\end{equation}
Then $G_{\MUB}^{4,3}$ is the extended nonlocal game where
\begin{equation}
    \pi(0, 0) = \pi(1, 1) = \pi(2, 2) = \pi(3, 3) = \frac{1}{4}
\end{equation}
and $V$ is such that
\begin{equation}
    V(0, 0|x, x), \ V(1, 1|x, x), \ V(2, 2,|x, x)
\end{equation}
represents a measurement with respect to the basis $\B_x$, for each $x \in
\{0,1,2,3\}$. Taking the description of $G_{\MUB}^{4,3}$, we can encode this as
an \texttt{ExtendedNonlocalGame} object in \toqito as is shown in
Figure~\ref{fig:mub_4_3}.

\begin{figure}[!htpb]
    \centering
    \lstinputlisting[language=Python]{code/mub_4_3.py}        
    \caption{Define the MUB$_{4, 3}$ extended nonlocal game.}
    \label{fig:mub_4_3}
\end{figure}

Now that we have encoded $G_{\MUB}^{4,3}$ as the variable
\texttt{mub\_4\_3\_game}, we can calculate both the unentangled and standard
quantum value as shown in
Figure~\ref{fig:mub_4_3_unentangled_quantum}.

\begin{figure}[!htpb]
    \centering
    \lstinputlisting[language=Python]{code/mub_4_3_unentangled_quantum.py}        
    \caption{Calculate the unentangled and standard quantum value of
    $G_{\MUB}^{4, 3}$}
    \label{fig:mub_4_3_unentangled_quantum}
\end{figure}

We can see that the unentangled value of $G_{\MUB}^{4,3}$ is given as
\begin{equation} 
    \omega(G_{\MUB}^{4,3}) = 
    \frac{3 + \sqrt{5}}{8} \approx 0.65409.  
\end{equation} 
However, running Figure~\ref{fig:mub_4_3_quantum} gives us a lower bound on the
standard quantum value of $G_{\MUB}^{4,3}$, which we can see is strictly higher
than $\omega(G_{\MUB}^{4,3})$.

It is uncertain what the optimal standard quantum strategy is for this game,
but the value of such a strategy is bounded as
follows~\cite{johnston2016extended}
\begin{equation}
    2/3 \geq \omega^*(G) \geq 0.6609.
\end{equation}

An open question in~\cite{russo2017thesis} and~\cite{johnston2016extended} is
whether there exists an example of an extended nonlocal game consisting of a
lesser number of questions and answers that exhibits the property of having
quantum advantage. It is known that for $\abs{\Sigma} = 2$, such a game does
not exist, but for $\abs{\Sigma} = 3$, it is unknown.

Using \toqito, we can show there does exist a game defined in terms of mutually
unbiased bases, specifically, the game $G_{\MUB}^{3,3}$ for which
\begin{equation}
    \omega(G_{\MUB}^{3,3}) < \omega^*(G_{\MUB}^{3,3}).
\end{equation}

\comment{TODO}

%-----------------------------------------------------------------------------%
\subsubsection{Non-signaling strategies for extended nonlocal games}
\label{sec:non_signaling_value_bb84_extended_nonlocal_game}
%-----------------------------------------------------------------------------%

A \emph{non-signaling strategy} for an extended nonlocal game consists of a
function
\begin{equation}
    K : \Gamma_A \times \Gamma_B \times \Sigma_A \times \Sigma_B \rightarrow
    \Pos(\R)
\end{equation}
such that
\begin{equation*}
    \sum_{a \in \Gamma_A} K(a,b|x,y) = \rho_b^y 
    \ \ \text{and} \ \
    \sum_{b \in \Gamma_B} K(a,b|x,y) = \sigma_a^x,
\end{equation*}
for all $x \in \Sigma_A$ and $y \in \Sigma_B$ where $\{\rho_a^y : y \in
\Sigma_B, b \in \Gamma_B\}$ and $\{\sigma_a^x : x \in \Sigma_A, a \in
\Gamma_A\}$ are collections of operators satisfying
\begin{equation}
    \sum_{a \in \Gamma_A} \sigma_a^x = 
    \tau = 
    \sum_{b \in \Gamma_B} \rho_b^y,
\end{equation}
for every choice of $x \in \Sigma_A$ and $y \in \Sigma_B$ and where $\tau \in
\Density(\R)$ is a density operator. For any extended nonlocal game, $G = (\pi,
V)$, the winning probability for a non-signaling strategy is given by
\begin{equation}
    \sum_{(x,y) \in \Sigma} \pi(x,y) \sum_{(a,b) \in \Gamma}
    \ip{V(a,b|x,y)}{K(a,b|x,y)}.
\end{equation}
The \emph{non-signaling value} of $G$ is denoted as $\omega_{ns}(G)$ which is
the supremum value of the winning probability of $G$ taken over all
non-signaling strategies for Alice and Bob.

\comment{TODO: Non-signaling value of BB84 game}

%-----------------------------------------------------------------------------%
\subsubsection{Parallel repetition for extended nonlocal games}
\label{}
%-----------------------------------------------------------------------------%

The $r$-fold parallel repetition of an extended nonlocal game, $G$, begins with
the referee accepting $r$ registers labelled as $\reg{R}_1, \ldots, \reg{R}_r$
from Alice and Bob where the registers contain the state
\begin{equation}
    \sigma \in \Density(\U \otimes \R_1 \otimes \cdots \otimes \R_r \otimes \V),
\end{equation}
and where the referee selects $r$ questions $(x_1, y_1) \in \Sigma_{A_1} \times
\Sigma_{B_1}, \ldots, (x_r, y_r) \in \Sigma_{A_r} \times \Sigma_{B_r}$
according to $\pi$. The referee sends $(x_1, y_1), \ldots, (x_r, y_r)$ to Alice
and Bob. The players return $r$ answers $(a_1, b_1) \in \Gamma_{A_1} \times
\Gamma_{B_1}, \ldots, (a_r, b_r) \in \Gamma_{A_r} \times \Gamma_{B_r}$ for each
question. The referee then perform a measurement from the set
% \begin{equation}
%     \begin{aligned}
%         \{V(a_1,b_1, \ldots, a_r, b_r|x_1, y_1, \ldots, x_r, y_r) &= \\
%         &V(a_1,b_1|x_1, y_1) \otimes \ldots \otimes V(a_r, b_r|x_r, y_r) : (a,b) \in
%         \Gamma, (x,y) \in \Sigma\}
%     \end{aligned}
% \end{equation}
Alice and Bob win the parallel repetition of $G$ if and only if their answers
win each of the $r$ instance of $G^r$.

\begin{figure}[!htpb]
    \centering
    \includegraphics[width=0.4\textwidth]{pics/extended_nonlocal_game_parallel_repetition.pdf}
    \caption{Parallel repetition of an extended nonlocal game.}
    \label{fig:extended_nonlocal_game_parallel_repetition}
\end{figure}

\comment{TODO: Non-signaling parallel rep of BB84 game}

%-----------------------------------------------------------------------------%
\subsection{Quantum state discrimination}
\label{sec:quantum_state_discrimination}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsubsection{Quantum state discrimination via PPT measurements}
\label{sec:}
%-----------------------------------------------------------------------------%

The problem of state discrimination with respect to PPT measurements can also
be framed as a semidefinite program whose optimal value corresponds to the
maximum probability of discriminating a state from an ensemble using any PPT
measurement~\cite{cosentino2013positive}. The dual problem of this optimization
problem is provided as
\begin{minipage}{1in}
\begin{equation} \label{eq:ppt-dual}
    \begin{aligned}
        \text{minimize:} 
        \quad & \frac{1}{N} \tr(H) \\ 
        \text{subject to:}
        \quad & H - \pt_{\X} (\rho_i) \in \Pos(\X \otimes \Y), \quad i = 1,
        \ldots, N, \\ & H \in \text{Herm}(\X \otimes \Y).
\end{aligned}
\end{equation}
\end{minipage}
Using \toqito, we can determine the optimal probability of distinguishing a
given state from an ensemble when restricted to using PPT measurements.

Consider the following Bell states
\begin{equation}
    \begin{aligned}
        \ket{\psi_0} = \frac{\ket{00} + \ket{11}}{\sqrt{2}}, & \ \ 
        \ket{\psi_1} = \frac{\ket{00} - \ket{11}}{\sqrt{2}}, \\
        \ket{\psi_2} = \frac{\ket{01} + \ket{10}}{\sqrt{2}}, & \ \ 
        \ket{\psi_3} = \frac{\ket{01} - \ket{10}}{\sqrt{2}}.
    \end{aligned}
\end{equation}
It was shown in~\cite{cosentino2013positive} and later extended
in~\cite{cosentino2013small} that for the following set of states
\begin{equation}\label{eq:ydy}
    \begin{aligned}
        \rho_0 = \ket{\psi_0} \ket{\psi_0} \bra{\psi_0} \bra{\psi_0}, \ \ 
        \rho_1 = \ket{\psi_2} \ket{\psi_1} \bra{\psi_2} \bra{\psi_1}, \\
        \rho_2 = \ket{\psi_3} \ket{\psi_1} \bra{\psi_3} \bra{\psi_1}, \ \
        \rho_3 = \ket{\psi_1} \ket{\psi_1} \bra{\psi_1} \bra{\psi_1}, \\
    \end{aligned}
\end{equation}
that the optimal probability of distinguishing via PPT measurements should
yield $7/8 \approx 0.875$. The ensemble of states from Equation~\eqref{eq:ydy}
were initially considered in~\cite{yu2012four}. In \toqito, we can calculate
the optimal probability of distinguishing via PPT measurements as shown in
Figure~\ref{fig:ppt_ydy}
\begin{figure}[!htpb]
    \centering
    \lstinputlisting[language=Python]{code/ppt_ydy.py}        
    \caption{Calculate the minimum-error probability of optimally
    distinguishing the states from Equation~\eqref{eq:ydy} via PPT
    measurements.}
    \label{fig:ppt_ydy}
\end{figure}

%-----------------------------------------------------------------------------%
\subsubsection{Quantum state discrimination via separable measurements}
\label{sec:}
%-----------------------------------------------------------------------------%
Unlike the set of PPT measurements, the structure of the set of separable
measurements is more complex.

\begin{minipage}{1in}
\begin{equation} \label{eq:sep-dual}
    \begin{aligned}
      \text{minimize:}\quad & \tr(H) \\
      \text{subject to:}\quad & H - p_i \rho_i \in \sep^*(\X : \Y), \quad i =
        1, \ldots, N, \\
      & H \in \Herm(\X \otimes \Y).
    \end{aligned}
\end{equation}    
\end{minipage}

%-----------------------------------------------------------------------------%
\section{Conclusion}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\section{Acknowledgements}
%-----------------------------------------------------------------------------%

\bibliography{main}
\clearpage
\end{document}

### 2021-04-08 docs/paper/code/bb84_game.py

@@ -1,0 +1,40 @@
+import numpy as np
+from toqito.states import basis
+from toqito.state_ops import pure_to_mixed
+from toqito.nonlocal_games.extended_nonlocal_game import ExtendedNonlocalGame
+
+# The basis: {|0>, |1>}:
+e_0 = basis(2, 0)
+e_1 = basis(2, 1)
+
+# The basis: {|+>, |->}:
+e_p = (e_0 + e_1) / np.sqrt(2)
+e_m = (e_0 - e_1) / np.sqrt(2)
+
+# Dimension of referee's measurement:
+dim = 2
+# The number of outputs for Alice and Bob:
+a_out, b_out = 2, 2
+# The number of inputs for Alice and Bob:
+a_in, b_in = 2, 2
+
+# The probability matrix.
+prob_mat = 1/2*np.identity(2)
+
+# Define the predicate matrix V(a,b|x,y):
+pred_mat = np.zeros([dim, dim, 
+                     a_out, b_out, 
+                     a_in, b_in])
+
+# V(0,0|0,0) = |0><0|
+pred_mat[:,:,0,0,0,0] = pure_to_mixed(e0)
+# V(1,1|0,0) = |1><1|
+pred_mat[:,:,1,1,0,0] = pure_to_mixed(e1)
+# V(0,0|1,1) = |+><+|
+pred_mat[:,:,0,0,1,1] = pure_to_mixed(ep)
+# V(1,1|1,1) = |-><-|
+pred_mat[:,:,1,1,1,1] = pure_to_mixed(em)
+
+# Extended nonlocal game based on BB84 game.
+bb84_game = ExtendedNonlocalGame(prob_mat,
+                                 pred_mat)

### 2021-04-08 docs/paper/code/bb84_game_quantum.py

@@ -1,0 +1,4 @@
+>>> bb84_game.quantum_value()
+0.8535533236834885
+
+

### 2021-04-08 docs/paper/code/bb84_game_unentangled.py

@@ -1,0 +1,2 @@
+>>> bb84_game.unentangled_value()
+0.8535533905544173

### 2021-04-08 docs/paper/code/chsh.py

@@ -1,0 +1,13 @@
+import numpy as np
+from toqito.nonlocal_games import xor_game
+
+# Probability matrix for each question pair:
+prob_mat = np.array([[1/4, 1/4],
+                     [1/4, 1/4]])
+
+# Encode winning conditions for the CHSH game:
+pred_mat = np.array([[0, 0],
+                    [0, 1]])
+
+# Define the CHSH XOR nonlocal game:
+chsh = xor_game.XORGame(prob_mat, pred_mat)

### 2021-04-08 docs/paper/code/chsh_classical_quantum.py

@@ -1,0 +1,7 @@
+>>> # Classical value of CHSH is 3/4:
+>>> chsh.classical_value()
+0.75
+
+>>> # Quantum value of CHSH is cos^2(pi/8):
+>>> chsh.quantum_value()
+8535533885683664

### 2021-04-08 docs/paper/code/chsh_parallel_repetition.py

@@ -1,0 +1,16 @@
+>>> # 2-fold parallel repetition of CHSH:
+>>> chsh_2 = xor_game.XORGame(prob_mat, 
+>>>                           pred_mat, 
+>>>                           reps=2)
+>>> # (cos^2(pi/8))^2 \approx 0.72853
+>>> chsh_2.quantum_value()
+0.7285533905932593
+
+
+>>> # 3-fold parallel repetition of CHSH:
+>>> chsh_3 = xor_game.XORGame(prob_mat, 
+>>>                           pred_mat,
+>>>                           reps=3)
+>>> # (cos^2(pi/8))^3 \approx 0.62186
+>>> chsh_3.quantum_value()
+0.6218592167690961

### 2021-04-08 docs/paper/code/mub.py

@@ -1,0 +1,27 @@
+from toqito.states import basis
+
+# Define |0>, |1>, |2>:
+dim = 3
+e_0 = basis(dim, 0)
+e_1 = basis(dim, 1) 
+e_2 = basis(dim, 2)
+
+# Define the mutually unbiased bases:
+z = np.exp((2*np.pi*1j)/dim)
+
+mub_0 = [e_0, e_1, e_2]
+mub_1 = [
+    (e_0 + e_1 + e_2)/np.sqrt(3),
+    (e_0 + z**2 * e_1 + z*e_2)/np.sqrt(3),
+    (e_0 + z*e_1 + z**2*e_2)/np.sqrt(3),
+]
+mub_2 = [
+    (e_0 + e_1 + z*e_2)/np.sqrt(3),
+    (e_0 + z**2 * e_1 + z**2 * e_2)/np.sqrt(3),
+    (e_0 + z*e_1 + e_2)/np.sqrt(3),
+]
+mub_3 = [
+    (e_0 + e_1 + z**2 * e_2)/np.sqrt(3),
+    (e_0 + z**2 * e_1 + e_2)/np.sqrt(3),
+    (e_0 + z*e_1 + z*e_2)/np.sqrt(3),
+]

### 2021-04-08 docs/paper/code/mub_3_3.py

@@ -1,0 +1,42 @@
+import numpy as np
+
+from toqito.states import basis
+from toqito.state_ops import pure_to_mixed
+from toqito.nonlocal_games.extended_nonlocal_game import ExtendedNonlocalGame
+
+prob_mat = 1 / 3 * np.identity(3)
+
+dim = 3
+e_0, e_1, e_2 = basis(dim, 0), basis(dim, 1), basis(dim, 2)
+
+z = np.exp((2 * np.pi * 1j)/dim)
+mub_1 = [
+    (e_0 + e_1 + e_2)/np.sqrt(3),
+    (e_0 + z**2 * e_1 + z*e_2)/np.sqrt(3),
+    (e_0 + z*e_1 + z**2*e_2)/np.sqrt(3),
+]
+mub_2 = [
+    (e_0 + e_1 + z*e_2)/np.sqrt(3),
+    (e_0 + z**2 * e_1 + z**2 * e_2)/np.sqrt(3),
+    (e_0 + z*e_1 + e_2)/np.sqrt(3),
+]
+mub_3 = [
+    (e_0 + e_1 + z**2 * e_2)/np.sqrt(3),
+    (e_0 + z**2 * e_1 + e_2)/np.sqrt(3),
+    (e_0 + z*e_1 + z*e_2)/np.sqrt(3),
+]
+
+mubs = [mub_1, mub_2, mub_3]
+
+num_in = 3
+num_out = 3
+pred_mat = np.zeros([dim, dim,
+                     num_out, num_out,
+                     num_in, num_in],
+                     dtype=complex)
+
+for i in range(num_in):
+    for o in range(num_out):
+        pred_mat[:,:,o,o,i,i] = pure_to_mixed(mubs[i][o])
+mub_3_3_game = ExtendedNonlocalGame(prob_mat, 
+                                    pred_mat)

### 2021-04-08 docs/paper/code/mub_4_3.py

@@ -1,0 +1,43 @@
+import numpy as np
+
+from toqito.states import basis
+from toqito.state_ops import pure_to_mixed
+from toqito.nonlocal_games.extended_nonlocal_game import ExtendedNonlocalGame
+
+prob_mat = 1 / 4 * np.identity(4)
+
+dim = 3
+e_0, e_1, e_2 = basis(dim, 0), basis(dim, 1), basis(dim, 2)
+
+z = np.exp((2 * np.pi * 1j)/dim)
+mub_0 = [e_0, e_1, e_2]
+mub_1 = [
+    (e_0 + e_1 + e_2)/np.sqrt(3),
+    (e_0 + z**2 * e_1 + z*e_2)/np.sqrt(3),
+    (e_0 + z*e_1 + z**2*e_2)/np.sqrt(3),
+]
+mub_2 = [
+    (e_0 + e_1 + z*e_2)/np.sqrt(3),
+    (e_0 + z**2 * e_1 + z**2 * e_2)/np.sqrt(3),
+    (e_0 + z*e_1 + e_2)/np.sqrt(3),
+]
+mub_3 = [
+    (e_0 + e_1 + z**2 * e_2)/np.sqrt(3),
+    (e_0 + z**2 * e_1 + e_2)/np.sqrt(3),
+    (e_0 + z*e_1 + z*e_2)/np.sqrt(3),
+]
+
+mubs = [mub_0, mub_1, mub_2, mub_3]
+
+num_in = 4
+num_out = 3
+pred_mat = np.zeros([dim, dim,
+                     num_out, num_out,
+                     num_in, num_in],
+                     dtype=complex)
+
+for i in range(num_in):
+    for o in range(num_out):
+        pred_mat[:,:,o,o,i,i] = pure_to_mixed(mubs[i][o])
+mub_4_3_game = ExtendedNonlocalGame(prob_mat, 
+                                    pred_mat)

### 2021-04-08 docs/paper/code/mub_4_3_quantum.py

@@ -1,0 +1,2 @@
+>>> mub_4_3_game.quantum_value()
+0.660931321341278

### 2021-04-08 docs/paper/code/mub_4_3_unentangled.py

@@ -1,0 +1,2 @@
+>>> mub_4_3_game.unentangled_value()
+0.6545084973280103

### 2021-04-08 docs/paper/code/mub_4_3_unentangled_quantum.py

@@ -1,0 +1,7 @@
+>>> # Unentangled value of MUB_{4,3}:
+>>> mub_4_3_game.unentangled_value()
+0.6545084973280103
+
+# Standard quantum value of MUB_{4,3}:
+>>> mub_4_3_game.quantum_value()
+0.660931321341278

### 2021-04-08 docs/paper/code/ppt_ydy.py

@@ -1,0 +1,23 @@
+import numpy as np
+
+from toqito.states import bell
+from toqito.state_ops import pure_to_mixed
+from toqito.state_opt import ppt_distinguishability
+
+# YDY vectors:
+x_0 = np.kron(bell(0), bell(0))
+x_1 = np.kron(bell(2), bell(1))
+x_2 = np.kron(bell(3), bell(1))
+x_3 = np.kron(bell(1), bell(1))
+
+# YDY density matrices:
+rho_0 = pure_to_mixed(x_0)
+rho_1 = pure_to_mixed(x_1)
+rho_2 = pure_to_mixed(x_2)
+rho_3 = pure_to_mixed(x_3)
+
+# Calculate PPT optimal value:
+states = [rho_0, rho_1, rho_2, rho_3]
+probs = [1/4, 1/4, 1/4, 1/4]
+
+ppt_distinguishability(states, probs)

### 2021-04-08 examples/opt_dist/ppt/min_error/four_bell_states.py

@@ -17,11 +17,12 @@ from qustop import Ensemble, State, OptDist
 
 
 # Construct the corresponding density matrices of the Bell states.
+dims = [2, 2]
 states = [
-    State(bell(0) * bell(0).conj().T, dims=[2, 2]),
-    State(bell(1) * bell(1).conj().T, dims=[2, 2]),
-    State(bell(2) * bell(2).conj().T, dims=[2, 2]),
-    State(bell(3) * bell(3).conj().T, dims=[2, 2])
+    State(bell(0) * bell(0).conj().T, dims),
+    State(bell(1) * bell(1).conj().T, dims),
+    State(bell(2) * bell(2).conj().T, dims),
+    State(bell(3) * bell(3).conj().T, dims)
 ]
 ensemble = Ensemble(states=states, probs=[1/4, 1/4, 1/4, 1/4])
 sd = OptDist(ensemble=ensemble, 

### 2021-04-08 examples/opt_dist/ppt/min_error/werner_hiding_pair.py

@@ -18,10 +18,13 @@ from qustop import Ensemble, State, OptDist
 
 
 dim = 2
-sigma_0 = (np.kron(np.identity(dim), np.identity(dim)) + swap_operator(dim)) / (dim * (dim + 1))
-sigma_1 = (np.kron(np.identity(dim), np.identity(dim)) - swap_operator(dim)) / (dim * (dim - 1))
+sigma_0 = (np.kron(np.identity(dim), np.identity(dim)) +
+           swap_operator(dim)) / (dim * (dim + 1))
+sigma_1 = (np.kron(np.identity(dim), np.identity(dim)) -
+           swap_operator(dim)) / (dim * (dim - 1))
 
-states = [State(sigma_0, [2, 2]), State(sigma_1, [2, 2])]
+states = [State(sigma_0, [dim, dim]),
+          State(sigma_1, [dim, dim])]
 ensemble = Ensemble(states)
 
 expected_val = 1 / 2 + 1 / (dim + 1)
@@ -32,5 +35,7 @@ sd = OptDist(ensemble=ensemble,
 
 sd.solve()
 
+# opt_ppt \approx 0.8333333333668715
 print(sd.value)
+# Closed-form expression is : 1/2 + 1/(dim+1) = 0.8333333333333333
 print(expected_val)

### 2021-04-08 qustop/opt_exclude/__init__.py

@@ -13,8 +13,4 @@
 # You should have received a copy of the GNU General Public License
 # along with this program.  If not, see <https://www.gnu.org/licenses/>.
 
-"""Optimal distinguishability of quantum states."""
-from qustop.opt_dist.ppt import PPT
-from qustop.opt_dist.positive import Positive
-from qustop.opt_dist.separable import Separable
-from qustop.opt_dist.opt_dist import OptDist
+"""Optimal exclusion of quantum states."""

### 2021-04-09 examples/opt_dist/ppt/min_error/entanglement_cost_nonorthogonal.py
Adding further to testing infrastructure.

@@ -35,11 +35,12 @@ eps = 0.215
 tau_state = np.sqrt((1 + eps) / 2) * np.kron(e_0, e_0) + np.sqrt((1 - eps) / 2) * np.kron(e_1, e_1)
 tau = tau_state * tau_state.conj().T
 
+dims = [2, 2, 2, 2]
 states = [
-    State(np.kron(rho_1, tau), [2, 2, 2, 2]),
-    State(np.kron(rho_2, tau), [2, 2, 2, 2]),
-    State(np.kron(rho_3, tau), [2, 2, 2, 2]),
-    State(np.kron(rho_4, tau), [2, 2, 2, 2])
+    State(np.kron(rho_1, tau), dims),
+    State(np.kron(rho_2, tau), dims),
+    State(np.kron(rho_3, tau), dims),
+    State(np.kron(rho_4, tau), dims)
 ]
 
 ensemble = Ensemble(states)

### 2021-04-09 qustop/opt_dist/opt_dist.py

@@ -69,7 +69,7 @@ class OptDist:
             if self.return_optimal_meas:
                 return 1.0, np.identity(self.ensemble.shape[0])
             else:
-                return 1.0
+                return 1.0, []
 
         # There is a closed-form expression for the distinguishability of two density matrices.
         if len(self.ensemble) == 2:
@@ -82,8 +82,18 @@ class OptDist:
         return None, []
 
     def solve(self):
+        """Depending on the measurement method selected, solve the appropriate optimization problem.
+        """
 
-        # self._optimal_value, self._optimal_measurements = self.pre_optimize()
+        # If `value` and `meas` were solved in the pre-optimization step, there's no need to
+        # perform any further calculations.
+        value, meas = self.pre_optimize()
+        if value is not None and self.return_optimal_meas is False:
+            self._optimal_value = value
+            return
+        elif value is not None and self.return_optimal_meas:
+            self._optimal_value, self._optimal_measurements = value, meas
+            return
 
         if self.dist_measurement == "ppt":
             opt = PPT(
@@ -126,3 +136,5 @@ class OptDist:
                 self._optimal_value, self._optimal_measurements = opt.solve()
             else:
                 self._optimal_value = opt.solve()
+        else:
+            raise ValueError(f"Measurement type {self.dist_method} not supported.")

### 2021-04-09 qustop/opt_dist/tests/test_opt_dist.py

@@ -1,0 +1,38 @@
+# Copyright (C) 2021 Vincent Russo
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <https://www.gnu.org/licenses/>.
+
+
+import numpy as np
+
+from qustop import Ensemble, State, OptDist
+from toqito.states import bell
+
+
+def test_invalid_ensemble():
+    """Invalid distinguishability measurement specified."""
+    with np.testing.assert_raises(ValueError):
+        dims = [2, 2]
+        rho_0 = State(bell(0) * bell(0).conj().T, dims)
+        rho_1 = State(bell(1) * bell(1).conj().T, dims)
+        rho_2 = State(bell(2) * bell(2).conj().T, dims)
+        ensemble = Ensemble([rho_0, rho_1, rho_2])
+
+        res = OptDist(
+            ensemble=ensemble,
+            dist_measurement="invalid",
+            dist_method="min-error",
+            return_optimal_meas=True,
+        )
+        res.solve()

### 2021-04-09 qustop/opt_dist/tests/test_positive.py

@@ -17,25 +17,13 @@
 import numpy as np
 
 from qustop import Ensemble, State, OptDist
-
-# Define single-qubit |0> and |1> basis states.
-e_0, e_1 = np.array([[1, 0]]).T, np.array([[0, 1]]).T
-
-# Define two-qubit |00>, |01>, |10>, and |11> basis states.
-e_00, e_01 = np.kron(e_0, e_0), np.kron(e_0, e_1)
-e_10, e_11 = np.kron(e_1, e_0), np.kron(e_1, e_1)
-
-# Define the Bell state vectors.
-b_0 = 1 / np.sqrt(2) * (e_00 + e_11)
-b_1 = 1 / np.sqrt(2) * (e_00 - e_11)
-b_2 = 1 / np.sqrt(2) * (e_01 + e_10)
-b_3 = 1 / np.sqrt(2) * (e_01 - e_10)
+from toqito.states import bell
 
 
 def test_state_distinguishability_one_state():
     """State distinguishability for single state."""
     dims = [2, 2]
-    rho = [State(b_0 * b_0.conj().T, dims)]
+    rho = [State(bell(0) * bell(0).conj().T, dims)]
     ensemble = Ensemble(rho)
 
     primal_res = OptDist(
@@ -60,7 +48,7 @@ def test_state_distinguishability_one_state():
 def test_state_distinguishability_one_state_vec():
     """State distinguishability for single vector state."""
     dims = [2, 2]
-    rho = [State(b_0, dims)]
+    rho = [State(bell(0), dims)]
     ensemble = Ensemble(rho)
 
     primal_res = OptDist(
@@ -85,7 +73,7 @@ def test_state_distinguishability_one_state_vec():
 def test_state_distinguishability_two_states():
     """State distinguishability for two state density matrices."""
     dims = [2, 2]
-    states = [State(e_00, dims), State(e_11, dims)]
+    states = [State(bell(0), dims), State(bell(1), dims)]
     probs = [1 / 2, 1 / 2]
     ensemble = Ensemble(states, probs)
 
@@ -111,7 +99,7 @@ def test_state_distinguishability_two_states():
 def test_unambiguous_state_distinguishability_two_states():
     """Unambiguous state distinguishability for two state density matrices."""
     dims = [2, 2]
-    states = [State(e_00, dims), State(e_11, dims)]
[…]

### 2021-04-09 qustop/opt_dist/tests/test_ppt.py

@@ -20,6 +20,22 @@ from toqito.perms import swap_operator
 from qustop import Ensemble, State, OptDist
 
 
+def test_ppt_distinguishability_one_state():
+    """PPT state distinguishability for single state."""
+    dims = [2, 2]
+    rho = [State(bell(0) * bell(0).conj().T, dims)]
+    ensemble = Ensemble(rho)
+
+    primal_res = OptDist(
+        ensemble=ensemble,
+        dist_measurement="pos",
+        dist_method="min-error",
+        return_optimal_meas=True,
+    )
+    primal_res.solve()
+    np.testing.assert_equal(np.isclose(primal_res.value, 1), True)
+
+
 def test_ppt_distinguishability_yyd_density_matrices():
     """
     PPT distinguishing the YYD states from [1] should yield `7/8 ~ 0.875`

### 2021-04-09 docs/paper/main.tex
Case sensitivity for docs.

@@
 %-----------------------------------------------------------------------------%
-\subsubsection{Quantum states}
-\label{sec:quantum_states}
-%-----------------------------------------------------------------------------%
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Properties of quantum states}
-\label{sec:properties_of_quantum_states}
-%-----------------------------------------------------------------------------%
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Distance metrics for quantum states}
-\label{sec:distance_metrics_for_quantum_states}
-%-----------------------------------------------------------------------------%
-
-%-----------------------------------------------------------------------------%
-\subsection{Channels}
-\label{sec:channels}
-%-----------------------------------------------------------------------------%
-
-A \emph{quantum channel} can be defined as a completely positive and trace
-preserving linear map.
-\\
-
-More formally, let $\X$ and $\Y$ represent complex Euclidean spaces and let
-$\Lin(\cdot)$ represent the set of linear operators. Then a quantum channel,
-$\Phi$ is defined as
-\begin{equation}
-    \Phi: \Lin(\X) \rightarrow \Lin(\Y)
-\end{equation}
-such that $\Phi$ is completely positive and trace preserving.
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Quantum channels}
-\label{sec:quantum_channels}
-%-----------------------------------------------------------------------------%
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Properties of quantum states}
-\label{sec:properties_of_quantum_states}
-%-----------------------------------------------------------------------------%
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Operations on quantum states}
-\label{sec:operations_on_quantum_states}
-%-----------------------------------------------------------------------------%
-
-%-----------------------------------------------------------------------------%
 \subsection{Measurements}

### 2021-04-30 docs/paper/main.tex
Adding to paper and tests

@@
 \def\MUB{\mathsf{MUB}}
+\def\qustop{\texttt{qustop}}
 
 \begin{document}
-\title{\toqito: Theory of quantum information toolkit}
+\title{\qustop: Quantum state optimizer}
 
@@
 \begin{abstract}
-    \toqito is an open source Python library for studying various objects in
-    quantum information, namely, states, channels, and measurements. \toqito
-    focuses on providing numerical tools to study problems pertaining to
-    entanglement theory, nonlocal games, and other aspects of quantum
-    information that are often associated with computer science. We illustrate
-    some of the core features of \toqito and show how it can be applied to
-    certain problems in quantum information. Using \toqito, we provide an
-    answer to one of the problems left open in~\cite{johnston2016extended} by
-    showing a more minimal example of an extended nonlocal game that possesses
-    a quantum advantage. We also make use of \toqito to numerically verify a
-    number of known results in the literature on subjects including quantum
-    state discrimination and nonlocal games. We hope that these numerical tools
-    can be used to aid researchers in further investigating these areas as well
-    as students studying quantum information.
 \end{abstract}
@@
 
-\comment{Intro}
-
-While there are many software packages that exist in the quantum software
-ecosystem, few of them have a core focus on quantum information.  Packages such
-as XX and XX specialize in quantum circuit synthesis and packages XX, XX, and
-XX center on problems pertaining to quantum machine learning~\cite{}. Software
-packages with a focus on quantum information .... For a more thorough survey on
-software packages pertaining to quantum information, consult the following
-survey~\cite{}.
-
-\toqito is an ... Documentation and tutorials are available on the \toqito
+Documentation and tutorials are available on the $\qustop$
 \href{https://github.com/vprusso/toqito}{GitHub repository}~\cite{toqito}.
@@
 
-Arguably, the core building blocks of quantum information consist of
-\emph{states}, \emph{channels}, and \emph{measurements}.\\
-
-\subsection{States}\label{sec:states}
-
-A \emph{quantum state} is a density operator
-\begin{equation}
-    \rho \in \Density(\X)
-\end{equation}
-where $\X$ is a complex Euclidean space and where $\Density(\cdot)$ represents
-the set of density matrices, that is, the set of matrices that are positive
-semidefinite with trace equal to $1$.
+%-----------------------------------------------------------------------------%
+\subsection{Quantum states and ensembles}\label{sec:ensembles}
+%-----------------------------------------------------------------------------%
 
 %-----------------------------------------------------------------------------%
-\subsection{Measurements}
-\label{sec:measurements}
+\section{Applications of qustop}
+\label{sec:applications}
 %-----------------------------------------------------------------------------%
 
-A \emph{measurement} can be defined as a function
-\begin{equation}
-    \mu: \Sigma \rightarrow \Pos(\X)
-\end{equation}
-satisfying
-\begin{equation}
-    \sum_{a \in \Sigma} \mu(a) = \I_{\X}
-\end{equation}
-where $\Sigma$ represents a set of measurement outcomes and where $\mu(a)$
-represents the measurement operator associated with outcome $a \in \Sigma$.
+%-----------------------------------------------------------------------------%
+\subsection{Calculating optimal probabilities of distinguishing quantum states}\label{sec:opt_dist}
+%-----------------------------------------------------------------------------%
 
 %-----------------------------------------------------------------------------%
-\section{Examples and Applications}
-\label{sec:examples_and_applications}
+\subsection{Global distinguishability}\label{sec:global}
 %-----------------------------------------------------------------------------%
 
-The \toqito software package \comment{TODO: elaborate}
+%-----------------------------------------------------------------------------%
+\subsection{PPT distinguishability}\label{sec:ppt}
+%-----------------------------------------------------------------------------%
 
 %-----------------------------------------------------------------------------%
-\subsection{Nonlocal games}\label{sec:nonlocal_games}
+\subsection{Separable distinguishability}\label{sec:separable}
 %-----------------------------------------------------------------------------%
 
-In this section, we are going to cover the notion of a \emph{nonlocal game}; a
-mathematical framework that abstractly models a physical system. The simplest
-instance of a nonlocal game involves two players--Alice and Bob, who are not
-allowed to communicate with each other once the game has started and who play
-cooperatively against an adversary referred to as the referee. \\
+%-----------------------------------------------------------------------------%
+\subsection{Calculating optimal probabilities of excluding quantum states}\label{sec:opt_exclude}
+%-----------------------------------------------------------------------------%
 
-A primary challenge that arises when studying these games is to determine the
-maximum probability with which Alice and Bob are able to achieve a winning
-outcome. \\
-
-The probability is dependent on the type of \emph{strategy} that Alice and Bob
-use in the game. A \emph{classical strategy} is one in which Alice and Bob have
-access to classical resources and play deterministically. The best that Alice
-and Bob can do using a classical strategy is known as the \emph{classical
-value} of the game.  Similarly, a \emph{quantum strategy} is one in which Alice
-and Bob have access to quantum resources in the form of a shared quantum state
-and respective sets of measurements. The best that Alice and Bob can do using a
-quantum strategy is known as the \emph{quantum value} of the game.
-\\
+%-----------------------------------------------------------------------------%
+\subsection{Calculating optimal probabilities of cloning quantum states}\label{sec:opt_clone}
+%-----------------------------------------------------------------------------%
 
@@
     \centering
-    \includegraphics[width=0.4\textwidth]{pics/nonlocal_game_quantum_strategy.pdf}
-    \caption{A nonlocal game}
-    \label{fig:nonlocal_game}
-\end{figure}
-
-More formally, a nonlocal game, $G$, is specified as a pair $(\pi, V)$ where
-$\pi$ is a probability distribution
-\begin{equation}
-    \pi : \Sigma_A \times \Sigma_B \rightarrow [0,1]
-\end{equation}
-on the Cartesian product of two alphabets $\Sigma_A$ and $\Sigma_B$, and $V$ is
-a function
-\begin{equation}
-    V : \Gamma_A \times \Gamma_B \times \Sigma_A \times \Sigma_B \rightarrow [0,1].
-\end{equation}
-We shall represent
-\begin{equation}
-    \Sigma = \Sigma_A \times \Sigma_B 
-    \ \ \text{and} \ \ 
-    \Gamma = \Gamma_A \times \Gamma_B
-\end{equation}
-to denote the respective sets of questions and answers for Alice and Bob.
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Classical strategies for nonlocal games}
-\label{sec:classical_strategies_for_nonlocal_games}
-%-----------------------------------------------------------------------------%
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Quantum strategies for nonlocal games}
-\label{sec:quantum_strategies_for_nonlocal_games}
-%-----------------------------------------------------------------------------%
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Non-signaling strategies for nonlocal games}
-\label{sec:non_signaling_strategies_for_nonlocal_games}
-%-----------------------------------------------------------------------------%
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Parallel repetition for nonlocal games}
-\label{sec:parallel_repeptitionfor_nonlocal_games}
-%-----------------------------------------------------------------------------%
-
-A game $G$ has the property of \emph{strong parallel repetition} if the value
-of the game raised to the power $r$ is equal to the value of running the game
-$r$ times.
-
-%-----------------------------------------------------------------------------%
-\subsection{XOR nonlocal games}
-\label{sec:xor_nonlocal_games}
-%-----------------------------------------------------------------------------%
-
-A \emph{two-player XOR nonlocal game} is a nonlocal game in which the winning
-condition is predicated on an XOR function~\cite{cleve2004consequences}.
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Example: The CHSH game}
-\label{sec:chsh_game}
-%-----------------------------------------------------------------------------%
-
-The \emph{CHSH game} is a two-player XOR game with the following probability
-distribution 
-\begin{equation}
-    \pi(x,y) = \frac{1}{4},
-\end{equation}
-and question and answer sets
-\begin{equation}
-    \begin{aligned}
-        (x,y) \in \Sigma_A \times \Sigma_B \quad \text{and} \quad (a,b) \in
-        \Gamma_A \times \Gamma_B,
-    \end{aligned}
-\end{equation}
-where 
-\begin{equation}
-    \Sigma_A = \Sigma_B = \Gamma_A = \Gamma_B = \{0,1\}.
-\end{equation}
-Alice and Bob win the CHSH game if and only if the following equation is
-satisfied
-\begin{equation}
-    a \oplus b = x \land y.
-\end{equation}
-For each question scenario, Table~\ref{tab:chsh_winning} provides what the
-winning condition must be equal to for each question tuple to induce a winning
-outcome.
-\begin{table}[!htpb]\label{tab:chsh_winning}
-    \begin{tabular}{|c|c|c|}
-        \hline
-        \textbf{$x$} & \textbf{$y$} & \textbf{$a \oplus b$} \\ \hline
-        0 & 0 & 0 \\ \hline
-        0 & 1 & 0 \\ \hline
-        1 & 0 & 0 \\ \hline
-        1 & 1 & 1 \\ \hline
-    \end{tabular}
-    \caption{Question pairs and respective winning outcomes for the CHSH game.}
-\end{table}
-In order to specify an XOR nonlocal game in \toqito, we will define two
-matrices:
-
-\begin{itemize}[noitemsep]
-    \item \texttt{prob\_mat}: A matrix whose $(x,y)^{th}$-entry corresponds to
-        the probability that Alice receives question $x$ and Bob receives
-        question $y$. \\
-    \item \texttt{pred\_mat}: A matrix whose $(x,y)^{th}$-entry corresponds to
-        the winning choice of $a$ and $b$ when Alice receives $x$ and Bob
-        receives $y$ from the referee.
-\end{itemize}
-
-We can encode the CHSH game, $G_{\CHSH} = (\pi, V)$, in \toqito by defining the
-\texttt{prob\_mat} and \texttt{pred\_mat} variables as is shown in
-Figure~\ref{fig:chsh}.
-
-\begin{figure}[!htpb]
-    \centering
-    \lstinputlisting[language=Python]{code/chsh.py}        
-    \caption{Define the CHSH XOR nonlocal game.}
-    \label{fig:chsh}
-\end{figure}
-
-That is, the \texttt{prob\_mat} variable encapsulates that each question pair
-$\{(0,0),(0,1),(1,0),(1,1)\}$ is equally likely. The \texttt{pred\_mat}
-variable indicates what the winning outcome of Alice and Bob should be. For
-instance, \texttt{pred\_mat[0][0] = 0} describes the scenario where Alice and
-Bob both receive $0$ as input. As we want to satisfy the winning condition $a
-\oplus b = x \land y$, we must have that $a \oplus b = 0$ to satisfy the case
-when both $x$ and $y$ are equal to zero. A similar logic can be followed to
-populate the remaining entries of the \texttt{pred\_mat} variable.
-
-What is very intriguing about the CHSH game is that it is an example of a
-nonlocal game where the players can do \emph{strictly} better if they make use
-of a quantum strategy instead of a classical one. It is known that the best
-that Alice and Bob can do when using a classical strategy is to win $G_{\CHSH}$
-with probability $3/4$, however, there exists a quantum strategy that enables
-Alice and Bob to win with a strictly higher probability of $\cos^2(\pi/8)
-\approx 0.8536$~\cite{cleve2004consequences}. We can numerically verify this
-fact in \toqito as is shown in Figure~\ref{fig:chsh_classical_quantum}
-
-\begin{figure}[!htpb]
-    \centering
-    \lstinputlisting[language=Python]{code/chsh_classical_quantum.py}        
-    \caption{Calculate the classical and quantum value of the CHSH XOR nonlocal
-    game.}
-    \label{fig:chsh_classical_quantum}
-\end{figure}
-
-Using \toqito, we can also compute how a given XOR nonlocal game behaves under
-parallel repetition. It holds from~\cite{cleve2008perfect} that the quantum
-value of any XOR nonlocal game obeys strong parallel repetition. That is, it
-holds that
-
-\begin{equation}
-    \omega^*(G^n) = \omega^*(G)^n 
-\end{equation}
-
-for any XOR nonlocal game, $G$. The \texttt{XORGame} class takes an optional
-argument, \texttt{reps}, that specifies how many parallel repetitions to run
-the game for (by default, this argument is equal to one). For instance, taking
-the \texttt{prob\_mat} and \texttt{pred\_mat} variables defined in
-Figure~\ref{fig:chsh} that characterize $G_{\CHSH}$, we can consider the value
-of the $r$-fold parallel repetition of $G_{\CHSH}$.
-Figure~\ref{fig:chsh_parallel_repetition} illustrates how one may compute the
-$2$-fold and $3$-fold parallel repetition of the CHSH game for the quantum
-value.
-
-\begin{figure}[!htpb]
-    \centering
-    \lstinputlisting[language=Python]{code/chsh_parallel_repetition.py}        
-    \caption{Calculate $2$-fold and $3$-fold parallel repetition of the CHSH game.}
-    \label{fig:chsh_parallel_repetition}
-\end{figure}
-
-%-----------------------------------------------------------------------------%
-\subsection{Extended nonlocal games}
-\label{sec:extended_nonlocal_games}
-%-----------------------------------------------------------------------------%
-
-In this section we shall define the concept of an \emph{extended nonlocal
-game}. Extended nonlocal games are a more general abstraction of nonlocal games
-wherein the referee, who previously only provided questions and answers to the
-players, now shares a state with the players and is able to perform a
-measurement on that shared state.
-\\
-
-Every extended nonlocal game has a \emph{value} associated to it. Analogously
-to nonlocal games, this value is a quantity that dictates how well the players
-can perform a task in the extended nonlocal game model when given access to
-certain resources. We will be using \toqito to calculate these quantities.
-\\
-
-Extended nonlocal games have a natural physical interpretation in the setting
-of tripartite steering~\cite{cavalcanti2015detection} and in device-independent
-quantum scenarios~\cite{tomamichel2013monogamy}, For more information on
-extended nonlocal games, please refer to~\cite{johnston2016extended,
-russo2017extended, russo2017thesis}.
-
-%-----------------------------------------------------------------------------%
-\subsubsection{The extended nonlocal game model}
-\label{sec:extended_nonlocal_game_model}
-%-----------------------------------------------------------------------------%
-
-An extended nonlocal game is similar to a nonlocal game in the sense that it is
-a cooperative game played between two players Alice and Bob against a referee.
-The game begins much like a nonlocal game, with the referee selecting and
-sending a pair of questions $(x,y)$ according to a fixed probability
-distribution. Once Alice and Bob receive $x$ and $y$, they respond with
-respective answers $a$ and $b$. Unlike a nonlocal game, the outcome of an
-extended nonlocal game is determined by measurements performed by the referee
-on its share of the state initially provided to it by Alice and Bob.
-
-\begin{figure}[!htpb]
-    \centering
-    \includegraphics[width=0.4\textwidth]{pics/extended_nonlocal_game.pdf}
-    \caption{An extended nonlocal game}
-    \label{fig:extended_nonlocal_game}
-\end{figure}
-
-Specifically, Alice and Bob's winning probability is determined by collections
-of measurements, $V(a,b|x,y) \in \Pos(\R)$, where $\R = \complex^m$ is a
-complex Euclidean space with $m$ denoting the dimension of the referee's
-quantum system--so if Alice and bob's response $(a,b)$ to the question pair
-$(x,y)$ leaves the referee's system in the quantum state
-\begin{equation}
-    \sigma_{a,b}^{x,y} \in \Density(\R),
-\end{equation}
-then their winning and losing probabilities are given by
-\begin{equation}
-    \ip{V(a,b|x,y)}{\sigma_{a,b}^{x,y}} \quad \text{and} \quad \ip{\I -
-    V(a,b|x,y)}{\sigma_{a,b}^{x,y}}.
-\end{equation}
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Strategies for extended nonlocal games}
-\label{sec:strategies_for_extended_nonlocal_games}
-%-----------------------------------------------------------------------------%
-
-An extended nonlocal game $G$ is defined by a pair $(\pi, V)$, where $\pi$ is a
-probability distribution of the form
-\begin{equation}
-    \pi: \Sigma_A \times \Sigma_B \rightarrow \left[0, 1\right]
-\end{equation}
-on the Cartesian product of two alphabets $\Sigma_A$ and $\Sigma_B$, and $V$ is
-a function of the form
-\begin{equation}
-    V: \Gamma_A \times \Gamma_B \times \Sigma_A \times \Sigma_B \rightarrow
-    \Pos(\R)
-\end{equation}
-for $\Sigma_A$ and $\Sigma_B$ as above, $\Gamma_A$ and $\Gamma_B$ being
-alphabets, and $\R$ refers to the referee's space. Just as in the case for
-nonlocal games, we shall use the convention that
-\begin{equation}
-    \Sigma = \Sigma_A \times \Sigma_B \quad \text{and} \quad \Gamma = \Gamma_A
-    \times \Gamma_B
-\end{equation}
-to denote the respective sets of questions asked to Alice and Bob and the sets
-of answers sent from Alice and Bob to the referee.
-
-When analyzing a strategy for Alice and Bob, it may be convenient to define a
-function
-\begin{equation}
-    K: \Gamma_A \times \Gamma_B \times \Sigma_A \times \Sigma_B \rightarrow
-    \Pos(\R).
-\end{equation}
-We can represent Alice and Bob's winning probability for an extended nonlocal game as
-\begin{equation}
-    \sum_{(x,y) \in \Sigma} \pi(x,y) \sum_{(a,b) \in \Gamma}
-    \ip{V(a,b|x,y)}{K(a,b|x,y)}.
-\end{equation}
-
-%-----------------------------------------------------------------------------%
-\subsubsection{The BB84 extended nonlocal game}
-%-----------------------------------------------------------------------------%
-
-The \emph{BB84 extended nonlocal game} is defined as follows. Let $\Sigma_A =
-\Sigma_B = \Gamma_A = \Gamma_B = \{0,1\}$, define
-\begin{equation}
-    \begin{aligned}
-        V(0,0|0,0) = 
-        \begin{pmatrix} 1 & 0 \\ 0 & 0 \end{pmatrix}, &\quad
-        V(0,0|1,1) = 
-        \frac{1}{2} \begin{pmatrix} 1 & 1 \\ 1 & 1 \end{pmatrix}, \\
-        V(1,1|0,0) = 
-        \begin{pmatrix} 0 & 0 \\ 0 & 1 \end{pmatrix}, &\quad
-        V(1,1|1,1) = 
-        \frac{1}{2} \begin{pmatrix} 1 & -1 \\ -1 & 1\end{pmatrix}
-    \end{aligned}
-\end{equation}
-define
-\begin{equation}
-    V(a,b|x,y) = \begin{pmatrix} 0 & 0 \\ 0 & 0 \end{pmatrix}
-\end{equation}
-for all $a \not= b$ or $x \not= y$, define $\pi(0, 0) = \pi(1, 1) =
-\frac{1}{2}$, and define $\pi(x,y) = 0$ if $x \not= y$.
-
-We can encode the BB84 extended nonlocal game, $G_{\BB84} = (\pi, V)$, in
-\numpy arrays where \texttt{prob\_mat} corresponds to the probability
-distribution $\pi$ and where \texttt{pred\_mat} corresponds to the operator
-$V$.
-
-\begin{figure}[!htpb]
-    \centering
-    \lstinputlisting[language=Python]{code/bb84_game.py}        
-    \caption{Define the BB84 extended nonlocal game.}
-    \label{fig:bb84_game}
-\end{figure}
-
-In the following sections, we will use the BB84 extended nonlocal game as an
-example for how one can define and compute the values of an extended nonlocal
-game in \toqito.
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Standard quantum strategies for extended nonlocal games}
-\label{sec:standard_quantum_strategies_for_extended_nonlocal_games}
-%-----------------------------------------------------------------------------%
-
-A \emph{standard quantum strategy} for an extended nonlocal game consists of
-finite-dimensional complex Euclidean spaces $\U$ for Alice and $\V$ for Bob, a
-quantum state $\sigma \in \Density(\U \otimes \R \otimes \V)$ and two
-collections of measurements
-\begin{equation*}
-    \{A_a^x : a \in \Gamma_A\} \subset \Pos(\U)
-    \ \ \text{and} \ \
-    \{B_b^y : b \in \Gamma_B\} \subset \Pos(\V),
-\end{equation*}
-for each $x \in \Sigma_A$ and $y \in \Sigma_B$. The winning probability for
-such a strategy in this game $G = (\pi, V)$ is given by
-\begin{equation}
-    \sum_{(x,y) \in \Sigma} \pi(x,y) \sum_{(a,b) \in \Gamma} \ip{A_a^x \otimes
-    V(a,b|x,y) \otimes B_b^y}{\sigma}
-\end{equation}
-For a given extended nonlocal game $G = (\pi, V)$, we write $\omega^*(G)$ to
-denote the \emph{standard quantum value} of $G$, which is the supremum value of
-Alice and Bob's winning probability over all standard quantum strategies.
-
-In~\cite{tomamichel2013monogamy}, it was shown that
-\begin{equation}
-    \omega^*(G_{\BB84}) = \cos^2(\pi/8) \approx 0.8536.
-\end{equation}
-We can verify this fact using \toqito in the following manner.
-\begin{figure}[!htpb]
-    \centering
-    \lstinputlisting[language=Python]{code/bb84_game_quantum.py}        
-    \caption{Calculate the standard quantum value of the BB84 extended nonlocal
-    game.}
-    \label{fig:bb84_game_quantum}
-\end{figure}
-
-\comment{note on calculating quantum values like nlg}
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Unentangled strategies for extended nonlocal games}
-\label{sec:unentangled_strategies_for_extended_nonlocal_games}
-%-----------------------------------------------------------------------------%
-
-An \emph{unentangled strategy} for an extended nonlocal game is simply a
-standard quantum strategy for which the state $\sigma \in \Density(\U \otimes
-\R \otimes \V)$ initially prepared by Alice and Bob is fully separable.
-\\
-
-For a given extended nonlocal game $G = (\pi, V)$, we write $\omega(G)$ to
-denote the \emph{unentangled value} of $G$, which is the supremum value for
-Alice and Bob's winning probability in $G$ over all unentangled strategies. The
-unentangled value of any extended nonlocal game, $G$, may be written as
-\begin{equation}
-    \omega(G) = \max_{f,g} \Bignorm{\sum_{(x,y) \in \Sigma} \pi(x,y) V(f(x),
-    g(y)|x,y)}
-\end{equation}
-where the maximum is over all functions $f : \Sigma_A \rightarrow \Gamma_A$ and
-$g : \Sigma_B \rightarrow \Gamma_B$.
-\\
-
-As we did with the standard quantum value in
-Section~\ref{sec:standard_quantum_strategies_for_extended_nonlocal_games}, we
-can similarly compute the unentangled value of $G_{\BB84}$:
-\begin{figure}[!htpb]
-    \centering
-    \lstinputlisting[language=Python]{code/bb84_game_unentangled.py}        
-    \caption{Calculate the standard quantum value of the BB84 extended nonlocal
-    game.}
-    \label{fig:bb84_game_unentangled}
-\end{figure}
-This agrees with what was shown in~\cite{tomamichel2013monogamy}
-and~\cite{johnston2016extended} that
-\begin{equation}
-    \omega(G_{\BB84}) = \cos^2(\pi/8) \approx 0.8536.
-\end{equation}
-Both the unentangled and standard quantum values for $G_{\BB84}$ are equal. In
-general though, there do exist extended nonlocal games where the quantum value
-is strictly higher than the unentangled value. Such an extended nonlocal where
-the referee's measurements are based on mutually unbiased bases was found
-in~\cite{johnston2016extended}.
-
-Recall that two orthonormal bases
-\begin{equation*}
-    \B_0 = \{u_a : a \in \Sigma\} \subset \complex^{\Sigma} \ \ 
-    \text{and} \ \
-    \B_1 = \{v_a : a \in \Sigma\} \subset \complex^{\Sigma}
-\end{equation*}
-are \emph{mutually unbiased} if and only if $\abs{\ip{u_a}{v_b}} =
-1/\sqrt{\Sigma}$ for all $a, b \in \Sigma$.  For $n \in \natural$, a set of
-orthonormal bases $\{\B_0, \ldots, \B_{n-1}\}$ are \emph{mutually unbiased
-bases} if and only if every basis is mutually unbiased with every other basis
-in the set, that is, $\B_x$ is mutually unbiased with $\B_{x^{\prime}}$ for all
-$x \not= x^{\prime}$ with $x, x^{\prime} \in \Sigma$.
-
-Let $G_{\MUB}^{\abs{\Sigma}, \abs{\Gamma}} = (\pi, V)$ represent the
-\emph{MUB$_{\abs{\Sigma}, \abs{\Gamma}}$ extended nonlocal game} where the
-measurement operators possessed by the referee are defined in terms of
-$\abs{\Sigma}$ mutually unbiased bases--each of dimension $\abs{\Gamma}$.
-
-As an example, consider $G_{\MUB}^{4, 3}$. Let $\Sigma_A =
-\Sigma_B = \{0, 1, 2, 3\}$ and $\Gamma_A = \Gamma_B = \{0, 1, 2\}$, let $\zeta
-= \exp(\frac{2\pi i}{3})$ and consider the following four mutually unbiased
-bases:
-\begin{equation}
-    \begin{aligned}
-        \B_0 &= \{e_0, e_1, e_2\}, \\
-        \B_1 &= \{\frac{e_0 + e_1 + e_2}{\sqrt{3}}, 
-                  \frac{e_0 + \zeta^2 e_1 + \zeta e_2}{\sqrt{3}}, 
-                  \frac{e_0 + \zeta e_1 + \zeta^2 e_2}{\sqrt{3}}\}, \\
-        \B_2 &= \{\frac{e_0 + e_1 + \zeta e_2}{\sqrt{3}},
-                  \frac{e_0 + \zeta^2 e_1 + \zeta^2e_2}{\sqrt{3}},
-                  \frac{e_0 + \zeta e_1 + e_2}{\sqrt{3}}\}, \\
-        \B_3 &= \{\frac{e_0 + e_1 + \zeta^2 e_2}{\sqrt{3}},
-                  \frac{e_0 + \zeta^2 e_1 + e_2}{\sqrt{3}},
-                  \frac{e_0 + \zeta e_1 + \zeta e_2}{\sqrt{3}}\}.
-    \end{aligned}
-\end{equation}
-Then $G_{\MUB}^{4,3}$ is the extended nonlocal game where
-\begin{equation}
-    \pi(0, 0) = \pi(1, 1) = \pi(2, 2) = \pi(3, 3) = \frac{1}{4}
-\end{equation}
-and $V$ is such that
-\begin{equation}
-    V(0, 0|x, x), \ V(1, 1|x, x), \ V(2, 2,|x, x)
-\end{equation}
-represents a measurement with respect to the basis $\B_x$, for each $x \in
-\{0,1,2,3\}$. Taking the description of $G_{\MUB}^{4,3}$, we can encode this as
-an \texttt{ExtendedNonlocalGame} object in \toqito as is shown in
-Figure~\ref{fig:mub_4_3}.
-
-\begin{figure}[!htpb]
-    \centering
-    \lstinputlisting[language=Python]{code/mub_4_3.py}        
-    \caption{Define the MUB$_{4, 3}$ extended nonlocal game.}
-    \label{fig:mub_4_3}
-\end{figure}
-
-Now that we have encoded $G_{\MUB}^{4,3}$ as the variable
-\texttt{mub\_4\_3\_game}, we can calculate both the unentangled and standard
-quantum value as shown in
-Figure~\ref{fig:mub_4_3_unentangled_quantum}.
-
-\begin{figure}[!htpb]
-    \centering
-    \lstinputlisting[language=Python]{code/mub_4_3_unentangled_quantum.py}        
-    \caption{Calculate the unentangled and standard quantum value of
-    $G_{\MUB}^{4, 3}$}
-    \label{fig:mub_4_3_unentangled_quantum}
-\end{figure}
-
-We can see that the unentangled value of $G_{\MUB}^{4,3}$ is given as
-\begin{equation} 
-    \omega(G_{\MUB}^{4,3}) = 
-    \frac{3 + \sqrt{5}}{8} \approx 0.65409.  
-\end{equation} 
-However, running Figure~\ref{fig:mub_4_3_quantum} gives us a lower bound on the
-standard quantum value of $G_{\MUB}^{4,3}$, which we can see is strictly higher
-than $\omega(G_{\MUB}^{4,3})$.
-
-It is uncertain what the optimal standard quantum strategy is for this game,
-but the value of such a strategy is bounded as
-follows~\cite{johnston2016extended}
-\begin{equation}
-    2/3 \geq \omega^*(G) \geq 0.6609.
-\end{equation}
-
-An open question in~\cite{russo2017thesis} and~\cite{johnston2016extended} is
-whether there exists an example of an extended nonlocal game consisting of a
-lesser number of questions and answers that exhibits the property of having
-quantum advantage. It is known that for $\abs{\Sigma} = 2$, such a game does
-not exist, but for $\abs{\Sigma} = 3$, it is unknown.
-
-Using \toqito, we can show there does exist a game defined in terms of mutually
-unbiased bases, specifically, the game $G_{\MUB}^{3,3}$ for which
-\begin{equation}
-    \omega(G_{\MUB}^{3,3}) < \omega^*(G_{\MUB}^{3,3}).
-\end{equation}
-
-\comment{TODO}
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Non-signaling strategies for extended nonlocal games}
-\label{sec:non_signaling_value_bb84_extended_nonlocal_game}
-%-----------------------------------------------------------------------------%
-
-A \emph{non-signaling strategy} for an extended nonlocal game consists of a
-function
-\begin{equation}
-    K : \Gamma_A \times \Gamma_B \times \Sigma_A \times \Sigma_B \rightarrow
-    \Pos(\R)
-\end{equation}
-such that
-\begin{equation*}
-    \sum_{a \in \Gamma_A} K(a,b|x,y) = \rho_b^y 
-    \ \ \text{and} \ \
-    \sum_{b \in \Gamma_B} K(a,b|x,y) = \sigma_a^x,
-\end{equation*}
-for all $x \in \Sigma_A$ and $y \in \Sigma_B$ where $\{\rho_a^y : y \in
-\Sigma_B, b \in \Gamma_B\}$ and $\{\sigma_a^x : x \in \Sigma_A, a \in
-\Gamma_A\}$ are collections of operators satisfying
-\begin{equation}
-    \sum_{a \in \Gamma_A} \sigma_a^x = 
-    \tau = 
-    \sum_{b \in \Gamma_B} \rho_b^y,
-\end{equation}
-for every choice of $x \in \Sigma_A$ and $y \in \Sigma_B$ and where $\tau \in
-\Density(\R)$ is a density operator. For any extended nonlocal game, $G = (\pi,
-V)$, the winning probability for a non-signaling strategy is given by
-\begin{equation}
-    \sum_{(x,y) \in \Sigma} \pi(x,y) \sum_{(a,b) \in \Gamma}
-    \ip{V(a,b|x,y)}{K(a,b|x,y)}.
-\end{equation}
-The \emph{non-signaling value} of $G$ is denoted as $\omega_{ns}(G)$ which is
-the supremum value of the winning probability of $G$ taken over all
-non-signaling strategies for Alice and Bob.
-
-\comment{TODO: Non-signaling value of BB84 game}
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Parallel repetition for extended nonlocal games}
-\label{}
-%-----------------------------------------------------------------------------%
-
-The $r$-fold parallel repetition of an extended nonlocal game, $G$, begins with
-the referee accepting $r$ registers labelled as $\reg{R}_1, \ldots, \reg{R}_r$
-from Alice and Bob where the registers contain the state
-\begin{equation}
-    \sigma \in \Density(\U \otimes \R_1 \otimes \cdots \otimes \R_r \otimes \V),
-\end{equation}
-and where the referee selects $r$ questions $(x_1, y_1) \in \Sigma_{A_1} \times
-\Sigma_{B_1}, \ldots, (x_r, y_r) \in \Sigma_{A_r} \times \Sigma_{B_r}$
-according to $\pi$. The referee sends $(x_1, y_1), \ldots, (x_r, y_r)$ to Alice
-and Bob. The players return $r$ answers $(a_1, b_1) \in \Gamma_{A_1} \times
-\Gamma_{B_1}, \ldots, (a_r, b_r) \in \Gamma_{A_r} \times \Gamma_{B_r}$ for each
-question. The referee then perform a measurement from the set
-% \begin{equation}
-%     \begin{aligned}
-%         \{V(a_1,b_1, \ldots, a_r, b_r|x_1, y_1, \ldots, x_r, y_r) &= \\
-%         &V(a_1,b_1|x_1, y_1) \otimes \ldots \otimes V(a_r, b_r|x_r, y_r) : (a,b) \in
-%         \Gamma, (x,y) \in \Sigma\}
-%     \end{aligned}
-% \end{equation}
-Alice and Bob win the parallel repetition of $G$ if and only if their answers
-win each of the $r$ instance of $G^r$.
-
-\begin{figure}[!htpb]
-    \centering
-    \includegraphics[width=0.4\textwidth]{pics/extended_nonlocal_game_parallel_repetition.pdf}
-    \caption{Parallel repetition of an extended nonlocal game.}
-    \label{fig:extended_nonlocal_game_parallel_repetition}
-\end{figure}
-
-\comment{TODO: Non-signaling parallel rep of BB84 game}
-
-%-----------------------------------------------------------------------------%
-\subsection{Quantum state discrimination}
-\label{sec:quantum_state_discrimination}
-%-----------------------------------------------------------------------------%
-
-%-----------------------------------------------------------------------------%
-\subsubsection{Quantum state discrimination via PPT measurements}
-\label{sec:}
-%-----------------------------------------------------------------------------%
-
-The problem of state discrimination with respect to PPT measurements can also
-be framed as a semidefinite program whose optimal value corresponds to the
-maximum probability of discriminating a state from an ensemble using any PPT
-measurement~\cite{cosentino2013positive}. The dual problem of this optimization
-problem is provided as
-\begin{minipage}{1in}
-\begin{equation} \label{eq:ppt-dual}
-    \begin{aligned}
-        \text{minimize:} 
-        \quad & \frac{1}{N} \tr(H) \\ 
-        \text{subject to:}
-        \quad & H - \pt_{\X} (\rho_i) \in \Pos(\X \otimes \Y), \quad i = 1,
-        \ldots, N, \\ & H \in \text{Herm}(\X \otimes \Y).
-\end{aligned}
-\end{equation}
-\end{minipage}
-Using \toqito, we can determine the optimal probability of distinguishing a
-given state from an ensemble when restricted to using PPT measurements.
-
-Consider the following Bell states
-\begin{equation}
-    \begin{aligned}
-        \ket{\psi_0} = \frac{\ket{00} + \ket{11}}{\sqrt{2}}, & \ \ 
-        \ket{\psi_1} = \frac{\ket{00} - \ket{11}}{\sqrt{2}}, \\
-        \ket{\psi_2} = \frac{\ket{01} + \ket{10}}{\sqrt{2}}, & \ \ 
-        \ket{\psi_3} = \frac{\ket{01} - \ket{10}}{\sqrt{2}}.
-    \end{aligned}
-\end{equation}
-It was shown in~\cite{cosentino2013positive} and later extended
-in~\cite{cosentino2013small} that for the following set of states
-\begin{equation}\label{eq:ydy}
-    \begin{aligned}
-        \rho_0 = \ket{\psi_0} \ket{\psi_0} \bra{\psi_0} \bra{\psi_0}, \ \ 
-        \rho_1 = \ket{\psi_2} \ket{\psi_1} \bra{\psi_2} \bra{\psi_1}, \\
-        \rho_2 = \ket{\psi_3} \ket{\psi_1} \bra{\psi_3} \bra{\psi_1}, \ \
-        \rho_3 = \ket{\psi_1} \ket{\psi_1} \bra{\psi_1} \bra{\psi_1}, \\
-    \end{aligned}
-\end{equation}
-that the optimal probability of distinguishing via PPT measurements should
-yield $7/8 \approx 0.875$. The ensemble of states from Equation~\eqref{eq:ydy}
-were initially considered in~\cite{yu2012four}. In \toqito, we can calculate
-the optimal probability of distinguishing via PPT measurements as shown in
-Figure~\ref{fig:ppt_ydy}
-\begin{figure}[!htpb]
-    \centering
-    \lstinputlisting[language=Python]{code/ppt_ydy.py}        
+    \lstinputlisting[language=Python]{code/indstinguishable_mes.py}        
     \caption{Calculate the minimum-error probability of optimally
@@
 %-----------------------------------------------------------------------------%
-Unlike the set of PPT measurements, the structure of the set of separable
-measurements is more complex.
-
-\begin{minipage}{1in}
-\begin{equation} \label{eq:sep-dual}
-    \begin{aligned}
-      \text{minimize:}\quad & \tr(H) \\
-      \text{subject to:}\quad & H - p_i \rho_i \in \sep^*(\X : \Y), \quad i =
-        1, \ldots, N, \\
-      & H \in \Herm(\X \otimes \Y).
-    \end{aligned}
-\end{equation}    
-\end{minipage}
 

### 2021-04-30 docs/paper/code/bb84_game.py

@@ -1,37 +1,0 @@
-import numpy as np
-from toqito.states import basis
-from toqito.state_ops import pure_to_mixed
-from toqito.nonlocal_games.extended_nonlocal_game import ExtendedNonlocalGame
-
-# The basis: {|0>, |1>}:
-e_0 = basis(2, 0)
-e_1 = basis(2, 1)
-
-# The basis: {|+>, |->}:
-e_p = (e_0 + e_1) / np.sqrt(2)
-e_m = (e_0 - e_1) / np.sqrt(2)
-
-# Dimension of referee's measurement:
-dim = 2
-# The number of outputs for Alice and Bob:
-a_out, b_out = 2, 2
-# The number of inputs for Alice and Bob:
-a_in, b_in = 2, 2
-
-# The probability matrix.
-prob_mat = 1 / 2 * np.identity(2)
-
-# Define the predicate matrix V(a,b|x,y):
-pred_mat = np.zeros([dim, dim, a_out, b_out, a_in, b_in])
-
-# V(0,0|0,0) = |0><0|
-pred_mat[:, :, 0, 0, 0, 0] = pure_to_mixed(e0)
-# V(1,1|0,0) = |1><1|
-pred_mat[:, :, 1, 1, 0, 0] = pure_to_mixed(e1)
-# V(0,0|1,1) = |+><+|
-pred_mat[:, :, 0, 0, 1, 1] = pure_to_mixed(ep)
-# V(1,1|1,1) = |-><-|
-pred_mat[:, :, 1, 1, 1, 1] = pure_to_mixed(em)
-
-# Extended nonlocal game based on BB84 game.
-bb84_game = ExtendedNonlocalGame(prob_mat, pred_mat)

### 2021-04-30 docs/paper/code/bb84_game_quantum.py

@@ -1,4 +1,0 @@
->>> bb84_game.quantum_value()
-0.8535533236834885
-
-

### 2021-04-30 docs/paper/code/bb84_game_unentangled.py

@@ -1,2 +1,0 @@
->>> bb84_game.unentangled_value()
-0.8535533905544173

### 2021-04-30 docs/paper/code/chsh.py

@@ -1,11 +1,0 @@
-import numpy as np
-from toqito.nonlocal_games import xor_game
-
-# Probability matrix for each question pair:
-prob_mat = np.array([[1 / 4, 1 / 4], [1 / 4, 1 / 4]])
-
-# Encode winning conditions for the CHSH game:
-pred_mat = np.array([[0, 0], [0, 1]])
-
-# Define the CHSH XOR nonlocal game:
-chsh = xor_game.XORGame(prob_mat, pred_mat)

### 2021-04-30 docs/paper/code/chsh_classical_quantum.py

@@ -1,7 +1,0 @@
->>> # Classical value of CHSH is 3/4:
->>> chsh.classical_value()
-0.75
-
->>> # Quantum value of CHSH is cos^2(pi/8):
->>> chsh.quantum_value()
-8535533885683664

### 2021-04-30 docs/paper/code/chsh_parallel_repetition.py

@@ -1,16 +1,0 @@
->>> # 2-fold parallel repetition of CHSH:
->>> chsh_2 = xor_game.XORGame(prob_mat, 
->>>                           pred_mat, 
->>>                           reps=2)
->>> # (cos^2(pi/8))^2 \approx 0.72853
->>> chsh_2.quantum_value()
-0.7285533905932593
-
-
->>> # 3-fold parallel repetition of CHSH:
->>> chsh_3 = xor_game.XORGame(prob_mat, 
->>>                           pred_mat,
->>>                           reps=3)
->>> # (cos^2(pi/8))^3 \approx 0.62186
->>> chsh_3.quantum_value()
-0.6218592167690961

### 2021-04-30 docs/paper/code/indstinguishable_mes.py

@@ -1,0 +1,38 @@
+import numpy as np
+from toqito.states import bell
+from qustop import State, Ensemble, OptDist
+
+
+# Define the maximally entangled states
+# from arXiv:1107.3224
+phi_0 = np.kron(bell(0), bell(0))
+phi_1 = np.kron(bell(2), bell(1))
+phi_2 = np.kron(bell(3), bell(1))
+phi_3 = np.kron(bell(1), bell(1))
+
+
+dims = [2, 2, 2, 2]
+rho_0 = phi_0 * phi_0.conj().T
+rho_1 = phi_1 * phi_1.conj().T
+rho_2 = phi_2 * phi_2.conj().T
+rho_3 = phi_3 * phi_3.conj().T
+
+ensemble = Ensemble(
+    [
+        State(rho_0, dims),
+        State(rho_1, dims),
+        State(rho_2, dims),
+        State(rho_3, dims),
+    ]
+)
+
+sd = OptDist(
+    ensemble=ensemble,
+    dist_measurement="ppt",
+    dist_method="min-error"
+)
+sd.solve()
+
+# The min-error probability of distinguishing
+# via PPT is equal to 7/8.
+print(sd.value)

### 2021-04-30 docs/paper/code/mub.py

@@ -1,27 +1,0 @@
-from toqito.states import basis
-
-# Define |0>, |1>, |2>:
-dim = 3
-e_0 = basis(dim, 0)
-e_1 = basis(dim, 1)
-e_2 = basis(dim, 2)
-
-# Define the mutually unbiased bases:
-z = np.exp((2 * np.pi * 1j) / dim)
-
-mub_0 = [e_0, e_1, e_2]
-mub_1 = [
-    (e_0 + e_1 + e_2) / np.sqrt(3),
-    (e_0 + z ** 2 * e_1 + z * e_2) / np.sqrt(3),
-    (e_0 + z * e_1 + z ** 2 * e_2) / np.sqrt(3),
-]
-mub_2 = [
-    (e_0 + e_1 + z * e_2) / np.sqrt(3),
-    (e_0 + z ** 2 * e_1 + z ** 2 * e_2) / np.sqrt(3),
-    (e_0 + z * e_1 + e_2) / np.sqrt(3),
-]
-mub_3 = [
-    (e_0 + e_1 + z ** 2 * e_2) / np.sqrt(3),
-    (e_0 + z ** 2 * e_1 + e_2) / np.sqrt(3),
-    (e_0 + z * e_1 + z * e_2) / np.sqrt(3),
-]

### 2021-04-30 docs/paper/code/mub_3_3.py

@@ -1,40 +1,0 @@
-import numpy as np
-
-from toqito.states import basis
-from toqito.state_ops import pure_to_mixed
-from toqito.nonlocal_games.extended_nonlocal_game import ExtendedNonlocalGame
-
-prob_mat = 1 / 3 * np.identity(3)
-
-dim = 3
-e_0, e_1, e_2 = basis(dim, 0), basis(dim, 1), basis(dim, 2)
-
-z = np.exp((2 * np.pi * 1j) / dim)
-mub_1 = [
-    (e_0 + e_1 + e_2) / np.sqrt(3),
-    (e_0 + z ** 2 * e_1 + z * e_2) / np.sqrt(3),
-    (e_0 + z * e_1 + z ** 2 * e_2) / np.sqrt(3),
-]
-mub_2 = [
-    (e_0 + e_1 + z * e_2) / np.sqrt(3),
-    (e_0 + z ** 2 * e_1 + z ** 2 * e_2) / np.sqrt(3),
-    (e_0 + z * e_1 + e_2) / np.sqrt(3),
-]
-mub_3 = [
-    (e_0 + e_1 + z ** 2 * e_2) / np.sqrt(3),
-    (e_0 + z ** 2 * e_1 + e_2) / np.sqrt(3),
-    (e_0 + z * e_1 + z * e_2) / np.sqrt(3),
-]
-
-mubs = [mub_1, mub_2, mub_3]
-
-num_in = 3
-num_out = 3
-pred_mat = np.zeros(
-    [dim, dim, num_out, num_out, num_in, num_in], dtype=complex
-)
-
-for i in range(num_in):
-    for o in range(num_out):
-        pred_mat[:, :, o, o, i, i] = pure_to_mixed(mubs[i][o])
-mub_3_3_game = ExtendedNonlocalGame(prob_mat, pred_mat)

### 2021-04-30 docs/paper/code/mub_4_3.py

@@ -1,41 +1,0 @@
-import numpy as np
-
-from toqito.states import basis
-from toqito.state_ops import pure_to_mixed
-from toqito.nonlocal_games.extended_nonlocal_game import ExtendedNonlocalGame
-
-prob_mat = 1 / 4 * np.identity(4)
-
-dim = 3
-e_0, e_1, e_2 = basis(dim, 0), basis(dim, 1), basis(dim, 2)
-
-z = np.exp((2 * np.pi * 1j) / dim)
-mub_0 = [e_0, e_1, e_2]
-mub_1 = [
-    (e_0 + e_1 + e_2) / np.sqrt(3),
-    (e_0 + z ** 2 * e_1 + z * e_2) / np.sqrt(3),
-    (e_0 + z * e_1 + z ** 2 * e_2) / np.sqrt(3),
-]
-mub_2 = [
-    (e_0 + e_1 + z * e_2) / np.sqrt(3),
-    (e_0 + z ** 2 * e_1 + z ** 2 * e_2) / np.sqrt(3),
-    (e_0 + z * e_1 + e_2) / np.sqrt(3),
-]
-mub_3 = [
-    (e_0 + e_1 + z ** 2 * e_2) / np.sqrt(3),
-    (e_0 + z ** 2 * e_1 + e_2) / np.sqrt(3),
-    (e_0 + z * e_1 + z * e_2) / np.sqrt(3),
-]
-
-mubs = [mub_0, mub_1, mub_2, mub_3]
-
-num_in = 4
-num_out = 3
-pred_mat = np.zeros(
-    [dim, dim, num_out, num_out, num_in, num_in], dtype=complex
-)
-
-for i in range(num_in):
-    for o in range(num_out):
-        pred_mat[:, :, o, o, i, i] = pure_to_mixed(mubs[i][o])
-mub_4_3_game = ExtendedNonlocalGame(prob_mat, pred_mat)

### 2021-04-30 docs/paper/code/mub_4_3_quantum.py

@@ -1,2 +1,0 @@
->>> mub_4_3_game.quantum_value()
-0.660931321341278

### 2021-04-30 docs/paper/code/mub_4_3_unentangled.py

@@ -1,2 +1,0 @@
->>> mub_4_3_game.unentangled_value()
-0.6545084973280103

### 2021-04-30 docs/paper/code/mub_4_3_unentangled_quantum.py

@@ -1,7 +1,0 @@
->>> # Unentangled value of MUB_{4,3}:
->>> mub_4_3_game.unentangled_value()
-0.6545084973280103
-
-# Standard quantum value of MUB_{4,3}:
->>> mub_4_3_game.quantum_value()
-0.660931321341278

### 2021-04-30 docs/paper/code/ppt_ydy.py

@@ -1,23 +1,0 @@
-import numpy as np
-
-from toqito.states import bell
-from toqito.state_ops import pure_to_mixed
-from toqito.state_opt import ppt_distinguishability
-
-# YDY vectors:
-x_0 = np.kron(bell(0), bell(0))
-x_1 = np.kron(bell(2), bell(1))
-x_2 = np.kron(bell(3), bell(1))
-x_3 = np.kron(bell(1), bell(1))
-
-# YDY density matrices:
-rho_0 = pure_to_mixed(x_0)
-rho_1 = pure_to_mixed(x_1)
-rho_2 = pure_to_mixed(x_2)
-rho_3 = pure_to_mixed(x_3)
-
-# Calculate PPT optimal value:
-states = [rho_0, rho_1, rho_2, rho_3]
-probs = [1 / 4, 1 / 4, 1 / 4, 1 / 4]
-
-ppt_distinguishability(states, probs)

### 2021-04-30 qustop/opt_dist/opt_dist.py

@@ -18,6 +18,8 @@ from typing import Any, List
 import cvxpy
 import numpy as np
 
+from toqito.state_metrics import trace_norm
+
 from qustop.core import Ensemble
 from qustop.opt_dist import Positive, PPT, Separable
 
@@ -71,9 +73,33 @@ class OptDist:
             else:
                 return 1.0, []
 
-        # There is a closed-form expression for the distinguishability of two density matrices.
         if len(self.ensemble) == 2:
+            # If the states are mutually orthogonal and both pure states, they are perfectly distinguishable
+            # arXiv:0007098.
+            if self.ensemble.is_mutually_orthogonal and self.ensemble[0].is_pure and self.ensemble[1].is_pure:
+                return 1.0
+
+            # In any case, there is a closed-form expression for the distinguishability of two density matrices.
             # TODO:
+            else:
+                return 1/2 + trace_norm(self.ensemble.probs[0] * self.ensemble.density_matrices[0] -
+                                        self.ensemble.probs[1] * self.ensemble.density_matrices[1])
+
+        if len(self.ensemble) == 3:
+            # Check if ensemble is in :math:`\mathbb{C}^2 \otimes \mathbb{C}^2`:
+            if len(self.ensemble.dims) == 2 and self.ensemble.dims[0] == self.ensemble.dims == 2:
+                # If two out of the three states are product states and all three states are pure then according to
+                # arXiv:0202034, the states are perfectly distinguishable.
+                # TODO
+                pass
+            pass
+
+        if len(self.ensemble) == 4:
+            # If ensemble is in :math:`\mathbb{C}^2 \otimes \mathbb{C}^2` and all states are product states, the
+            # ensemble is perfectly distinguishable according to arXiv:0202034
+            # TODO
+            if len(self.ensemble.dims) == 2 and self.ensemble.dims[0] == self.ensemble.dims == 2:
+                pass
             pass
 
         # # If the states are mutually orthogonal, it is possible to perfectly distinguish.

### 2021-04-30 qustop/opt_dist/positive.py

@@ -116,20 +116,41 @@ class Positive:
         """Calculate dual problem for the positive (global) distinguishability SDP.
 
         The dual problem for the min-error case is defined in equation-21 from arXiv:1707.02571.
-        The dual problem for the unambiguous case is defined in equation- from arXiv:.
+        The dual problem for the unambiguous case is defined in equation-4.73
+        from https://uwspace.uwaterloo.ca/bitstream/handle/10012/9572/Cosentino_Alessandro.pdf.
         """
         num_measurements = (
             len(self._states) + 1
             if self._dist_method == "unambiguous"
             else len(self._states)
         )
-
+        constraints = []
         y_var = cvxpy.Variable(self._ensemble.shape, hermitian=True)
 
-        constraints = [
-            (y_var - self._probs[i] * self._states[i]) >> 0
-            for i in range(num_measurements)
-        ]
+        if self._dist_method == "min-error":
+            constraints = [
+                (y_var - self._probs[i] * self._states[i]) >> 0
+                for i in range(num_measurements)
+            ]
+
+        # This implements the dual problem (equation-4.73) from
+        # https://uwspace.uwaterloo.ca/bitstream/handle/10012/9572/Cosentino_Alessandro.pdf:
+        if self._dist_method == "unambiguous":
+            scalar_vars = [
+                [cvxpy.Variable() for i, _ in enumerate(self._states)]
+                for j, _ in enumerate(self._states)
+            ]
+
+            for j, _ in enumerate(self._states):
+                sum_val = 0
+                for i, _ in enumerate(self._states):
+                    if i != j:
+                        sum_val += (
+                            cvxpy.real(scalar_vars[i][j])
+                            * self._probs[i]
+                            * self._states[i]
+                        )
+                constraints.append(y_var - self._probs[j] * self._states[j] + sum_val >> 0)
 
         objective = cvxpy.Minimize(cvxpy.trace(cvxpy.real(y_var)))
         problem = cvxpy.Problem(objective, constraints)

### 2021-04-30 qustop/opt_dist/separable.py

@@ -60,7 +60,6 @@ class Separable:
         self._probs = self._ensemble.probs
 
         self._dims = self._ensemble.dims
-        self._sys = [i for i in self._ensemble.systems if i % 2 != 0]
 
         self.dim_x, self.dim_y = self._ensemble[0].shape
         self.dim_list = self._ensemble[0].dims
@@ -125,12 +124,12 @@ class Separable:
                 == x_var[k]
             )
             constraints.append(partial_transpose(x_var[k], 1, dim_list) >> 0)
-            constraints.append(meas[k] >> 0)
-            constraints.append(x_var[k] >> 0)
             for sys in range(3, self._level + 2):
                 constraints.append(
                     partial_transpose(x_var[k], sys, dim_list) >> 0
                 )
+            constraints.append(meas[k] >> 0)
+            constraints.append(x_var[k] >> 0)
 
         constraints.append(cvxpy.sum(meas) == np.identity(self._ensemble.shape[0]))
 
@@ -144,22 +143,18 @@ class Separable:
         return opt_val, meas
 
     def dual_problem(self) -> float:
-        dim_x, dim_y = self._states[0].shape
-
         constraints = []
-        Q = []
-        R = []
-        S = []
-        Z = []
+        q_vars = []
+        r_vars = []
+        s_vars = []
+        z_vars = []
 
-        dim = int(np.log2(dim_x))
-        dim_list = [dim] * (self._level + 1)
-
-        dim_xy = dim_x
+        dim = int(np.log2(self.dim_x))
+        dim_list = (2 + self._level - 1) * [dim]
         dim_xyy = np.prod(dim_list)
+
         sym = symmetric_projection(dim, self._level)
         print(f"DIM: {dim}")
-        print(f"DIM_XY: {dim_xy}")
         print(f"DIM_XYY: {dim_xyy}")
         print(f"DIM_LIST: {dim_list}")
 
@@ -168,35 +163,35 @@ class Separable:
         else:
             dim_yp = dim * (self._level - 1)
 
-        h_var = cvxpy.Variable((dim_xy, dim_xy), hermitian=True)
+        h_var = cvxpy.Variable(self._ensemble.shape, hermitian=True)
         for k, _ in enumerate(self._states):
-            Q.append(cvxpy.Variable((dim_xy, dim_xy), hermitian=True))
-            R.append(cvxpy.Variable((dim_xyy, dim_xyy), hermitian=True))
-            S.append(cvxpy.Variable((dim_xyy, dim_xyy), hermitian=True))
[…]

### 2021-04-30 qustop/opt_dist/tests/test_positive.py

@@ -112,13 +112,12 @@ def test_unambiguous_state_distinguishability_two_states():
     primal_res.solve()
     np.testing.assert_equal(np.isclose(primal_res.value, 1), True)
 
-
-# dual_res = OptDist(ensemble=ensemble,
-#                    dist_measurement="pos",
-#                    dist_method="unambiguous",
-#                    return_optimal_meas=False)
-# dual_res.solve()
-# np.testing.assert_equal(np.isclose(dual_res.value, 0), True)
+    dual_res = OptDist(ensemble=ensemble,
+                       dist_measurement="pos",
+                       dist_method="unambiguous",
+                       return_optimal_meas=False)
+    dual_res.solve()
+    np.testing.assert_equal(np.isclose(dual_res.value, 1), True)
 
 
 def test_state_distinguishability_ydy_density_matrices():

### 2021-04-30 qustop/opt_exclude/opt_exclude.py

@@ -1,0 +1,98 @@
+# Copyright (C) 2021 Vincent Russo
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <https://www.gnu.org/licenses/>.
+
+from typing import Any, List
+
+import cvxpy
+import numpy as np
+
+from toqito.matrix_ops import tensor
+from qustop.core import Ensemble
+
+
+class OptExclude:
+    def __init__(
+        self,
+        ensemble: Ensemble,
+        **kwargs: Any,
+    ):
+        self._ensemble = ensemble
+
+        self._return_optimal_meas = kwargs.get("return_optimal_meas", True)
+        self._solver = kwargs.get("solver", "SCS")
+        self._verbose = kwargs.get("verbose", False)
+        self._eps = kwargs.get("eps", 1e-8)
+
+        self._optimal_value = None
+        self._optimal_measurements: List[np.ndarray] = []
+
+        self._states = self._ensemble.density_matrices
+        self._probs = self._ensemble.probs
+
+    @property
+    def value(self) -> float:
+        return self._optimal_value
+
+    @property
+    def measurements(self) -> List[np.ndarray]:
+        if isinstance(self._optimal_measurements[0], cvxpy.Variable):
+            self._optimal_measurements = self.convert_measurements(
+                self._optimal_measurements
+            )
+        return self._optimal_measurements
+
+    @staticmethod
+    def convert_measurements(measurements) -> List[np.ndarray]:
+        return [measurements[i].value for i in range(len(measurements))]
+
+    def solve(self) -> None:
+        """Depending on the measurement method selected, solve the appropriate optimization problem."""
+        dim = len(self._states[0]) ** 3
+
+        # Construct the following operator:
+        #                                ___               ___
+        # Q = ∑_{k=1}^N p_k |ψ_k ⊗ ψ_k ⊗ ψ_k> <ψ_k ⊗ ψ_k ⊗ ψ_k|
+        q_a = np.zeros((dim, dim))
+        for k, state in enumerate(self._states):
[…]

### 2021-05-04 docs/paper/main.tex
Adding more to paper.

@@
-\documentclass[nofootinbib,superscriptaddress,a4paper,twocolumn,longbibliography,floatfix,pra]{revtex4-2}
-\usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
+% pdflatex -s main.tex && bibtex main.aux && pdflatex -s main.tex -o main.pdf && open main.pdf
+\documentclass[11pt]{article}
 
-\usepackage{enumitem}
+%-----------------------------------------------------------------------------%
+% Fonts and symbols:
+%-----------------------------------------------------------------------------%
 
+\usepackage{mathpazo}
 \usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{latexsym}
+\usepackage{mathtools}
+\usepackage{listings}
+
+%-----------------------------------------------------------------------------%
+% Margins and page layout:
+%-----------------------------------------------------------------------------%
+
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{pdfpagemode=UseNone}
+\frenchspacing
+
+%-----------------------------------------------------------------------------%
+% Theorem-like environments:
+%-----------------------------------------------------------------------------%
+
 \usepackage{amsthm}
-\usepackage{mathtools}
-\usepackage{physics}
-\usepackage{xcolor}
-\usepackage{graphicx}
-\usepackage[left=23mm,right=13mm,top=35mm,columnsep=15pt]{geometry} 
-\usepackage{adjustbox}
-\usepackage{placeins}
-\usepackage[T1]{fontenc}
-\usepackage{lipsum}
-\usepackage{csquotes}
+\newtheorem{theorem}{Theorem}
+\newtheorem{observation}{Observation}
+\newtheorem{conjecture}{Conjecture}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{prop}[theorem]{Proposition}
+\newtheorem{cor}[theorem]{Corollary}
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{example}[theorem]{Example}
 
-\usepackage{listings}
+%-----------------------------------------------------------------------------%
+% Other packages:
+%-----------------------------------------------------------------------------%
+
+\usepackage{authblk}
+\usepackage{tikz}
+\usetikzlibrary{calc,positioning}
+\usepackage{mdframed}
+
+\mdfdefinestyle{figstyle}{
+  linecolor=black!7,
+  backgroundcolor=black!7,
+  innertopmargin=10pt,
+  innerleftmargin=25pt,
+  innerrightmargin=25pt,
+  innerbottommargin=10pt
+}
+
+\definecolor{White}{rgb}{1,1,1}
+\definecolor{Black}{rgb}{0,0,0}
+\definecolor{LightGray}{rgb}{.81,.81,.81}
+\colorlet{ChannelColor}{LightGray}
+\colorlet{ChannelTextColor}{Black}
+\colorlet{ReadoutColor}{White}
+
 \usepackage{xcolor}
@@
 
-\usepackage{xspace}
-\newcommand{\expect}[2]{\ensuremath{\langle #1 \rangle_{#2}}}
-
-\setlength{\parindent}{0cm}
-
-\usepackage[pdftex, pdftitle={Article}, pdfauthor={Author}]{hyperref} % For hyperlinks in the PDF
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
 %-----------------------------------------------------------------------------%
@@
 \newcommand{\negsmallspace}{\mspace{-1.5mu}}
+\newcommand{\op}[1]{\operatorname{#1}}
+\newcommand{\tr}{\operatorname{Tr}}
 \newcommand{\pt}{\operatorname{T}}
-\newcommand{\ppt}{\operatorname{PPT}}
-\newcommand{\sep}{\operatorname{Sep}}
+\newcommand{\POS}{\operatorname{POS}}
+\newcommand{\PPT}{\operatorname{PPT}}
+\newcommand{\SEP}{\operatorname{SEP}}
+\newcommand{\rank}{\operatorname{rank}}
 \renewcommand{\int}{\operatorname{int}}
@@
 
-\renewcommand{\tr}{\operatorname{Tr}}
 \renewcommand{\t}{{\scriptscriptstyle\mathsf{T}}}
 
-\renewcommand{\abs}[1]{\lvert #1 \rvert}
+\newcommand{\abs}[1]{\lvert #1 \rvert}
 \newcommand{\bigabs}[1]{\bigl\lvert #1 \bigr\rvert}
@@
 
-\renewcommand{\ip}[2]{\langle #1 , #2\rangle}
+\newcommand{\ip}[2]{\langle #1 , #2\rangle}
 \newcommand{\bigip}[2]{\bigl\langle #1, #2 \bigr\rangle}
@@
 
+\newcommand{\norm}[1]{\lVert\tinyspace #1 \tinyspace\rVert}
 \newcommand{\bignorm}[1]{\bigl\lVert\tinyspace #1 \tinyspace\bigr\rVert}
@@
 
+\newcommand{\ket}[1]{
+  \lvert\microspace #1 \microspace \rangle}
+
 \newcommand{\bigket}[1]{
@@
   \Biggl\lvert\microspace #1 \microspace \Biggr\rangle}
+
+\newcommand{\bra}[1]{
+  \langle\microspace #1 \microspace \rvert}
 
@@
 
-\newcommand{\I}{\mathbb{I}}
+\newcommand{\I}{\mathbb{1}}
 
@@
 \newcommand{\complex}{\mathbb{C}}
+\newcommand{\real}{\mathbb{R}}
 \renewcommand{\natural}{\mathbb{N}}
@@
 
-\usepackage{FiraSans}
+\newcommand{\qustop}{\texttt{qustop}}
+
 \newcommand{\poly}{\mathit{poly}}
-\newcommand{\toqitofont}{%
-	\fontfamily{FiraSans}%
-	\selectfont}
 
-\newcommand{\toqito}{ $|${\toqitofont toqito}$\rangle$\xspace}
-\newcommand{\numpy}{\texttt{numpy}\xspace}
-\newcommand{\tequila}{\textsc{toqito}}
 \newenvironment{mylist}[1]{\begin{list}{}{
@@
 \newcommand{\no}{\text{no}}
+\newcommand{\opt}{\text{opt}}
+\newcommand{\LOCC}{\text{LOCC}}
 
@@
 
-\def\BB84{\mathsf{BB84}}
-\def\CHSH{\mathsf{CHSH}}
-\def\MUB{\mathsf{MUB}}
-\def\qustop{\texttt{qustop}}
+\DeclareFixedFont{\ttb}{T1}{txtt}{bx}{n}{10}
+\DeclareFixedFont{\ttm}{T1}{txtt}{m}{n}{10}
+\definecolor{deepblue}{rgb}{0,0,0.5}
+\definecolor{deepred}{rgb}{0.6,0,0}
+\definecolor{deepgreen}{rgb}{0,0.5,0}
+\newcommand\cppstyle{\lstset{
+language=C++,
+basicstyle=\ttm,
+otherkeywords={uint8_t, __m256i, size_t, ASSERT_TRUE, EXPECT_TRUE, TEST, BENCHMARK},
+keywordstyle=\ttb\color{deepblue},
+emphstyle=\ttb\color{deepblue},
+stringstyle=\color{deepgreen},
+commentstyle=\fontfamily{txtt}\selectfont\color{gray},
+showstringspaces=false,
+literate={*}{{\char42}}1
+         {-}{{\char45}}1
+}}
+\lstnewenvironment{cpp}[1][]
+{\cppstyle\lstset{#1}}{}
+\newcommand\pythonstyle{\lstset{
+language=python,
+basicstyle=\ttm,
+morekeywords={assert,as,echo},
+keywordstyle=\ttb\color{deepblue},
+emphstyle=\ttb\color{deepblue},
+stringstyle=\color{deepgreen},
+commentstyle=\fontfamily{txtt}\selectfont\color{gray},
+showstringspaces=false,
+literate={*}{{\char42}}1
+         {-}{{\char45}}1
+}}
+\lstnewenvironment{python}[1][]
+{\pythonstyle\lstset{#1}}{}
+
+\makeatletter
+\let\@fnsymbol\@arabic
+\makeatother
+
+%-----------------------------------------------------------------------------%
+% Main document
+%-----------------------------------------------------------------------------%
 
 \begin{document}
-\title{\qustop: Quantum state optimizer}
 
-\author{Vincent Russo}
-\email[E-mail:]{vincentrusso1@gmail.com}
-\affiliation{-}
+\title{\LARGE\bf \qustop: Quantum state optimizer}
 
-\date{\today}
+\author[1]{Vincent Russo}
 
-\begin{abstract}
-\end{abstract}
+\renewcommand\Affilfont{\normalsize\itshape}
+\renewcommand\Authfont{\large}
+\setlength{\affilsep}{6mm}
+\renewcommand\Authand{\rule{10mm}{0mm}}
 
@@
 
-%-----------------------------------------------------------------------------%
+\begin{abstract}
+    The \qustop\ package is an open-source Python module for studying various
+    quantum state optimization scenarios including calculating optimal values
+    for quantum state distinguishability, quantum state exclusion, and quantum
+    state cloning.
+\end{abstract}
+
+%------------------------------------------------------------------------------%
 \section{Introduction}
-\label{sec:introduction}
-%-----------------------------------------------------------------------------%
+\label{sec:intro}
+%------------------------------------------------------------------------------%
 
-Documentation and tutorials are available on the $\qustop$
-\href{https://github.com/vprusso/toqito}{GitHub repository}~\cite{toqito}.
+%------------------------------------------------------------------------------%
+\section{Definitions}
+\label{sec:definitions}
+%------------------------------------------------------------------------------%
 
-%-----------------------------------------------------------------------------%
-\section{Fundamental objects}
-\label{sec:fundemental_objects}
-%-----------------------------------------------------------------------------%
+It holds that
+\begin{equation}
+    0 \leq \omega_t(\eta, \LOCC) \leq \omega_t(\eta, \SEP) \leq \omega_t(\eta, \PPT) \leq \omega_t(\eta, \POS) \leq 1
+\end{equation}
+for all $t \in [U, M]$.
 
-%-----------------------------------------------------------------------------%
-\subsection{Quantum states and ensembles}\label{sec:ensembles}
-%-----------------------------------------------------------------------------%
+It holds that
+\begin{equation}
+    0 \leq \omega_U(\eta, T) \leq \omega_M(\eta, T) \leq 1
+\end{equation}
+for all $T \in [\LOCC, \SEP, \PPT, \POS]$.
 
-%-----------------------------------------------------------------------------%
-\section{Applications of qustop}
-\label{sec:applications}
-%-----------------------------------------------------------------------------%
+The four Bell states $\ket{\psi_0}, \ldots, \ket{\psi_3} \in \complex^2 \otimes
+\complex^2$ are defined as
 
-%-----------------------------------------------------------------------------%
-\subsection{Calculating optimal probabilities of distinguishing quantum states}\label{sec:opt_dist}
-%-----------------------------------------------------------------------------%
+\begin{equation}
+    \begin{aligned}
+        \ket{\psi_0} = \frac{1}{\sqrt{2}} \left(\ket{00} + \ket{11} \right), &\quad
+        \ket{\psi_1} = \frac{1}{\sqrt{2}} \left(\ket{01} + \ket{10} \right), \\
+        \ket{\psi_2} = \frac{1}{\sqrt{2}} \left(\ket{01} - \ket{10} \right), &\quad
+        \ket{\psi_3} = \frac{1}{\sqrt{2}} \left(\ket{00} - \ket{11} \right).
+    \end{aligned}
+\end{equation}
 
-%-----------------------------------------------------------------------------%
-\subsection{Global distinguishability}\label{sec:global}
-%-----------------------------------------------------------------------------%
+\subsection{Minimum-error distinguishability of four two-qubit states via PPT measurements}
 
-%-----------------------------------------------------------------------------%
-\subsection{PPT distinguishability}\label{sec:ppt}
-%-----------------------------------------------------------------------------%
+\begin{theorem}\label{thm:min_error_four_state_two_qubit_ppt}
+    Let $\X = \Y = \complex^2$. For any PPT measurement $\{ P_1, P_2, P_3, P_4
+    \} \subset \PPT(\X : \Y)$, the success probability of correctly
+    discriminating the states corresponding to the set 
+	\begin{equation}
+        \left\{ 
+            \ket{\phi_n^{(1)}},
+            \ket{\phi_n^{(2)}},
+            \ket{\phi_m^{(3)}},
+            \ket{\phi_m^{(4)}} 
+        \right\} \subset 
+        \left(\X \otimes \Y \right)
+	\end{equation}
+    assuming a uniform distribution $p_1 = p_2 = p_3 = p_4 = 1/4$, is at most
+    \begin{equation}
+        \frac{1}{2} \left(1 + \frac{n+m}{2}\right)
+    \end{equation}
+    for all $n \in [0, 1]$ and $m \in [0, 1]$.
+\end{theorem}
+\begin{proof}
+	Define the Hermitian operator
+	\begin{equation}
+        H_{n,m} = \frac{1}{2}
+        \begin{pmatrix}
+            1+n & 0 & 0 & 0 \\
+            0 & 1+m & 0 & 0 \\
+            0 & 0 & 1+m & 0 \\
+            0 & 0 & 0 & 1+n
+        \end{pmatrix}
+        \in \Herm(\X \otimes \Y).
+	\end{equation}
+	It holds that
+	\begin{equation}
+        \frac{1}{4}\tr(H_{n,m}) = \frac{1}{2} \left(1 + \frac{n+m}{2}\right).
+	\end{equation}
+    We now desire to show that 
+    \begin{equation}
+        \begin{aligned}
+            H_{n,m} - \pt_{\X}\left(\phi_n^{(1)}\right) \in \Pos(\X \otimes\Y),
+            &\quad
+            H_{n,m} - \pt_{\X}\left(\phi_n^{(2)}\right) \in \Pos(\X \otimes\Y), \\
+            H_{n,m} - \pt_{\X}\left(\phi_m^{(3)}\right) \in \Pos(\X \otimes\Y),
+            &\quad
+            H_{n,m} - \pt_{\X}\left(\phi_n^{(4)}\right) \in \Pos(\X \otimes\Y),
+        \end{aligned}
+    \end{equation}
+    for all $n \in [0, 1]$ and $m \in [0, 1]$. Observe that
+    \begin{equation}\label{eq:partial-transpose-states}
+        \begin{aligned}
+            \pt_{\X}\left(\phi_n^{(1)}\right) = 
+            \begin{pmatrix}
+                \alpha^2 & 0 & 0 & 0 \\
+                0 & 0 & \alpha\beta & 0 \\
+                0 & \alpha\beta & 0 & 0 \\
+                0 & 0 & 0 & \beta^2
+            \end{pmatrix}, &\quad 
+            \pt_{\X}\left(\phi_n^{(2)}\right) = 
+            \begin{pmatrix}
+                \beta^2 & 0 & 0 & 0 \\
+                0 & 0 & -\alpha\beta & 0 \\
+                0 & -\alpha\beta & 0 & 0 \\
+                0 & 0 & 0 & \alpha^2
+            \end{pmatrix}, \\ 
+            \pt_{\X}\left(\phi_m^{(3)}\right) = 
+            \begin{pmatrix}
+                0 & 0 & 0 & \gamma\delta \\
+                0 & \gamma^2 & 0 & 0 \\
+                0 & 0 & \delta^2 & 0 \\
+                \gamma\delta & 0 & 0 & 0
+            \end{pmatrix}, &\quad 
+            \pt_{\X} \left(\phi_m^{(4)}\right) = 
+            \begin{pmatrix}
+                0 & 0 & 0 & -\gamma\delta \\
+                0 & \delta^2 & 0 & 0 \\
+                0 & 0 & \gamma^2 & 0 \\
+                -\gamma\delta & 0 & 0 & 0
+            \end{pmatrix}.
+        \end{aligned}
+    \end{equation}
+    We can represent $H_{n,m}$ as
+    \begin{equation}
+        H_{n,m} = 
+        \begin{pmatrix}
+            \alpha^2 & 0 & 0 & 0 \\
+            0 & \gamma^2 & 0 & 0 \\
+            0 & 0 & \gamma^2 & 0 \\
+            0 & 0 & 0 & \alpha^2
+        \end{pmatrix}
+    \end{equation}
+    since it holds that
+    \begin{equation}
+        \alpha^2 = \left(\sqrt{\frac{1+n}{2}}\right)^2 = \frac{1 + n}{2} 
+        \quad \text{and} \quad 
+        \gamma^2 = \left(\sqrt{\frac{1+m}{2}}\right)^2 = \frac{1 + m}{2}.
+    \end{equation}
+    Consider $k=1$ and observe that
+    \begin{equation}
+        H_{n,m} - \pt_{\X}\left(\phi_n^{(1)}\right) = 
+        \begin{pmatrix}
+            \alpha^2 - \alpha^2 & 0 & 0 & 0 \\
+            0 & \gamma^2 & -\alpha\beta & 0 \\
+            0 & -\alpha\beta & \gamma^2 & 0 \\
+            0 & 0 & 0 & \alpha^2 - \beta^2
+        \end{pmatrix}
+    \end{equation}
+    which is positive semidefinite as $0 \leq \beta \leq \alpha \leq 1$ and $0
+    \leq \delta \leq \gamma \leq 1$ for all $n \in [0,1]$ and $m \in [0,1]$. A
+    similar observation can be made for $k = 2, 3, 4$
+\end{proof}
 
-%-----------------------------------------------------------------------------%
-\subsection{Separable distinguishability}\label{sec:separable}
-%-----------------------------------------------------------------------------%
+For completeness, we provide the following code listing that makes use of
+\qustop to encode the setting from
+Theorem~\ref{thm:min_error_four_state_two_qubit_ppt}.
 
-%-----------------------------------------------------------------------------%
-\subsection{Calculating optimal probabilities of excluding quantum states}\label{sec:opt_exclude}
-%-----------------------------------------------------------------------------%
+\begin{figure}[!htpb]
+    \centering
+    \lstinputlisting[language=Python]{code/four_state_two_qubit_ppt.py}
+    \caption{}
+    \label{fig:ppt_four_state_two_qubit}
+\end{figure}
 
-%-----------------------------------------------------------------------------%
-\subsection{Calculating optimal probabilities of cloning quantum states}\label{sec:opt_clone}
-%-----------------------------------------------------------------------------%
+\subsubsection*{Example: Indistinguishable maximally entangled states}
+
+Consider the following ensemble in $\complex^4 \otimes \complex^4$ defined as
+\begin{equation}\label{eq:ydy_ensemble}
+    \eta = \left\{ \left(\frac{1}{4}, \ket{\psi_0} \otimes \ket{\psi_0} \right), 
+                  \left(\frac{1}{4}, \ket{\psi_2} \otimes \ket{\psi_1} \right),
+                  \left(\frac{1}{4}, \ket{\psi_3} \otimes \ket{\psi_1} \right),
+                  \left(\frac{1}{4}, \ket{\psi_1} \otimes \ket{\psi_1} \right) 
+            \right\} \subset \complex^4 \otimes \complex^4.
+\end{equation}
+In~\cite{yu2012four}, these states were shown to not be perfectly
+distinguishable via PPT measurements, although the optimal probability with
+which one is able to distinguish via PPT measurements was left as an open
+question. This question was resolved in~\cite{cosentino2013positive}, where it
+was shown that $\omega_M(\eta, \PPT) = 7/8$.
+
+In~\cite{cosentino2013positive} it was also shown that $\omega_U(\eta, \PPT) = 3/4$.
 
@@
     \lstinputlisting[language=Python]{code/indstinguishable_mes.py}
-    \caption{Calculate the minimum-error probability of optimally
-    distinguishing the states from Equation~\eqref{eq:ydy} via PPT
-    measurements.}
+    \caption{Calculate the minimum-error and unambiguous probabilities of
+    distinguishing the ensemble from Equation~\eqref{eq:ydy_ensemble} via PPT
+    measurements and separable measurements.}
     \label{fig:ppt_ydy}
@@
 
-%-----------------------------------------------------------------------------%
-\subsubsection{Quantum state discrimination via separable measurements}
-\label{sec:}
-%-----------------------------------------------------------------------------%
+\subsubsection*{Example: Entanglement cost of distinguishing Bell states}
 
-%-----------------------------------------------------------------------------%
-\section{Conclusion}
-%-----------------------------------------------------------------------------%
+One may ask whether the ability to distinguish a state can be improved by
+making use of an auxiliary resource state
+\begin{equation}
+    \ket{\tau_{\epsilon}} = \sqrt{\frac{1+\epsilon}{2}}\ket{00} + \sqrt{\frac{1-\epsilon}{2}},
+\end{equation}
+for some $\epsilon \in [0, 1]$.
 
-%-----------------------------------------------------------------------------%
-\section{Acknowledgements}
-%-----------------------------------------------------------------------------%
+\bibliographystyle{alpha}
+\bibliography{refs}
 
-\bibliography{main}
-\clearpage
 \end{document}

### 2021-05-04 docs/paper/code/four_state_two_qubit_ppt.py

@@ -1,0 +1,29 @@
+import numpy as np
+from toqito.states import basis
+from qustop import Ensemble, OptDist, State
+
+n, m = 0, 0
+alpha, beta = np.sqrt((1 + n) / 2), np.sqrt((1 - n) / 2)
+gamma, delta = np.sqrt((1 + m) / 2), np.sqrt((1 - m) / 2)
+
+e_0, e_1 = basis(2, 0), basis(2, 1)
+
+dims = [2, 2]
+ensemble = Ensemble(
+    [
+        State(alpha * np.kron(e_0, e_0) + beta * np.kron(e_1, e_1), dims),
+        State(beta * np.kron(e_0, e_0) - alpha * np.kron(e_1, e_1), dims),
+        State(gamma * np.kron(e_0, e_1) + delta * np.kron(e_1, e_0), dims),
+        State(delta * np.kron(e_0, e_1) - gamma * np.kron(e_1, e_0), dims),
+    ]
+)
+
+# Determine the optimal probability of distinguishing
+# via PPT measurements with minimum error:
+ppt_min = OptDist(ensemble, "ppt", "min-error")
+ppt_min.solve()
+
+print(ppt_min.value)
+
+print(1 / 2 * (1 + (n + m) / 2))
+

### 2021-05-04 docs/paper/code/indstinguishable_mes.py

@@ -1,38 +1,32 @@
 import numpy as np
 from toqito.states import bell
-from qustop import State, Ensemble, OptDist
+from qustop import Ensemble, OptDist, State
 
-
-# Define the maximally entangled states
-# from arXiv:1107.3224
-phi_0 = np.kron(bell(0), bell(0))
-phi_1 = np.kron(bell(2), bell(1))
-phi_2 = np.kron(bell(3), bell(1))
-phi_3 = np.kron(bell(1), bell(1))
-
-
+# Define the ensemble initially defined in arXiv:1107.3224:
 dims = [2, 2, 2, 2]
-rho_0 = phi_0 * phi_0.conj().T
-rho_1 = phi_1 * phi_1.conj().T
-rho_2 = phi_2 * phi_2.conj().T
-rho_3 = phi_3 * phi_3.conj().T
-
 ensemble = Ensemble(
     [
-        State(rho_0, dims),
-        State(rho_1, dims),
-        State(rho_2, dims),
-        State(rho_3, dims),
+        State(np.kron(bell(0), bell(0)), dims),
+        State(np.kron(bell(2), bell(1)), dims),
+        State(np.kron(bell(3), bell(1)), dims),
+        State(np.kron(bell(1), bell(1)), dims),
     ]
 )
 
-sd = OptDist(
-    ensemble=ensemble,
-    dist_measurement="ppt",
-    dist_method="min-error"
-)
-sd.solve()
+# Determine the optimal probability of distinguishing
+# via PPT measurements with minimum error:
+ppt_min = OptDist(ensemble, "ppt", "min-error")
+ppt_min.solve()
+print(ppt_min.value)  # 7/8
 
-# The min-error probability of distinguishing
-# via PPT is equal to 7/8.
-print(sd.value)
+# Determine the optimal probability of distinguishing
+# via separable measurements with minimum-error:
+sep_min = OptDist(ensemble, "sep", "min-error")
+sep_min.solve()
+print(sep_min.value)  # 3/4
+
+# Determine the optimal probability of distinguishing
+# via PPT measurements unambiguously:
+ppt_unambig = OptDist(ensemble, "ppt", "unambiguous")
+ppt_unambig.solve()
+print(ppt_unambig.value)  # 3/4

### 2021-05-05 docs/paper/main.tex
Adding to tests, examples, and tutorials.

@@
     for quantum state distinguishability, quantum state exclusion, and quantum
-    state cloning.
+    state cloning. We showcase how \qustop \ can be used to verify known results
+    in the domain of quantum state distinguishability as well as how it can be
+    used as a numerical utility for new results. The \qustop \ package is
+    publicly accessible on GitHub at~\cite{}.
 \end{abstract}
@@
 \label{sec:definitions}
+%------------------------------------------------------------------------------%
+
+We assume the reader is familiar with the notions of quantum information as
+contained in~\cite{nielsen2002quantum} and~\cite{wilde2013quantum}. We will
+make use of the notation and terminology found in~\cite{watrous2018theory}.
+
+Let $\X = \complex^N$ denote a finite-dimensional complex Euclidean space with
+a fixed standard basis $\{\ket{1}, \ldots, \ket{N} \}$ for some positive
+integer $N$. We use sets $\Lin(\X), \Pos(\X), \Herm(\X), \Density(\X)$, and
+$\Unitary(\X)$ to represent the set of a linear operators, positive
+semidefinite operators, Hermitian operators, density operators, and unitary
+operators acting on the space $\X$.
+
+We begin by describing the setting of quantum state discrimination over an
+ensemble of quantum states. In this setting, we are provided with a collection
+of tuples (an ensemble)
+
+\begin{equation}
+    \{(p_1, \rho_1), \ldots, (p_N, \rho_N) \ \} \subset 
+    (\X_1 \otimes \Y_1) \otimes \cdots \otimes (\X_N \otimes \Y_N),
+\end{equation}
+where $\rho_i \in \Density(\X_i \otimes \Y_i)$ denotes a shared quantum state
+between two parties, Alice and Bob, indexed by $i$ and where $p_i$ denotes the
+probability with which $\rho_i$ is selected from the ensemble. The state
+discrimination procedure involves a random index $k \in \{1, \ldots, N\}$ being
+selected. Alice and Bob are then provided with the state $\rho_k$ where their
+goal is to determine the index $k$ by performing a measurement on their
+respective shared portion of the state.
+
+%------------------------------------------------------------------------------%
+\subsubsection*{Quantum states and ensembles}
+\label{sec:quantum_states_and_ensembles}
+%------------------------------------------------------------------------------%
+
+%------------------------------------------------------------------------------%
+\subsubsection*{Semidefinite programming}
+\label{sec:semidefinite_programming}
 %------------------------------------------------------------------------------%
@@
 \end{equation}
+
+%------------------------------------------------------------------------------%
+\section{Quantum state distinguishability}
+\label{sec:qsd}
+%------------------------------------------------------------------------------%
+
+%------------------------------------------------------------------------------%
+\subsubsection*{Example: Indistinguishable maximally entangled states}
+\label{sec:indistinguishable_mes}
+%------------------------------------------------------------------------------%
+
+Consider the following ensemble in $\complex^4 \otimes \complex^4$ defined as
+\begin{equation}\label{eq:ydy_ensemble}
+    \eta = \left\{ \left(\frac{1}{4}, \ket{\psi_0} \otimes \ket{\psi_0} \right), 
+                  \left(\frac{1}{4}, \ket{\psi_2} \otimes \ket{\psi_1} \right),
+                  \left(\frac{1}{4}, \ket{\psi_3} \otimes \ket{\psi_1} \right),
+                  \left(\frac{1}{4}, \ket{\psi_1} \otimes \ket{\psi_1} \right) 
+            \right\} \subset \complex^4 \otimes \complex^4.
+\end{equation}
+In~\cite{yu2012four}, these states were shown to not be perfectly
+distinguishable via PPT measurements, although the optimal probability with
+which one is able to distinguish via PPT measurements was left as an open
+question. This question was resolved in~\cite{cosentino2013positive}, where it
+was shown that $\omega_M(\eta, \PPT) = 7/8$.
+
+In~\cite{cosentino2013positive} it was also shown that $\omega_U(\eta, \PPT) = 3/4$.
+
+\begin{figure}[!htpb]
+    \centering
+    \lstinputlisting[language=Python]{code/indstinguishable_mes.py}
+    \caption{Calculate the minimum-error and unambiguous probabilities of
+    distinguishing the ensemble from Equation~\eqref{eq:ydy_ensemble} via PPT
+    measurements and separable measurements.}
+    \label{fig:ppt_ydy}
+\end{figure}
+
+%------------------------------------------------------------------------------%
+\subsubsection*{Example: Entanglement cost of distinguishing Bell states}
+\label{sec:entanglement_cost_bell}
+%------------------------------------------------------------------------------%
+
+One may ask whether the ability to distinguish a state can be improved by
+making use of an auxiliary resource state
+\begin{equation}
+    \ket{\tau_{\epsilon}} = \sqrt{\frac{1+\epsilon}{2}}\ket{00} + \sqrt{\frac{1-\epsilon}{2}},
+\end{equation}
+for some $\epsilon \in [0, 1]$.
 
@@
 
-\subsubsection*{Example: Indistinguishable maximally entangled states}
+%------------------------------------------------------------------------------%
+\section{Quantum state exclusion}
+\label{sec:qse}
+%------------------------------------------------------------------------------%
 
-Consider the following ensemble in $\complex^4 \otimes \complex^4$ defined as
-\begin{equation}\label{eq:ydy_ensemble}
-    \eta = \left\{ \left(\frac{1}{4}, \ket{\psi_0} \otimes \ket{\psi_0} \right), 
-                  \left(\frac{1}{4}, \ket{\psi_2} \otimes \ket{\psi_1} \right),
-                  \left(\frac{1}{4}, \ket{\psi_3} \otimes \ket{\psi_1} \right),
-                  \left(\frac{1}{4}, \ket{\psi_1} \otimes \ket{\psi_1} \right) 
-            \right\} \subset \complex^4 \otimes \complex^4.
-\end{equation}
-In~\cite{yu2012four}, these states were shown to not be perfectly
-distinguishable via PPT measurements, although the optimal probability with
-which one is able to distinguish via PPT measurements was left as an open
-question. This question was resolved in~\cite{cosentino2013positive}, where it
-was shown that $\omega_M(\eta, \PPT) = 7/8$.
-
-In~\cite{cosentino2013positive} it was also shown that $\omega_U(\eta, \PPT) = 3/4$.
-
-\begin{figure}[!htpb]
-    \centering
-    \lstinputlisting[language=Python]{code/indstinguishable_mes.py}
-    \caption{Calculate the minimum-error and unambiguous probabilities of
-    distinguishing the ensemble from Equation~\eqref{eq:ydy_ensemble} via PPT
-    measurements and separable measurements.}
-    \label{fig:ppt_ydy}
-\end{figure}
-
-\subsubsection*{Example: Entanglement cost of distinguishing Bell states}
-
-One may ask whether the ability to distinguish a state can be improved by
-making use of an auxiliary resource state
-\begin{equation}
-    \ket{\tau_{\epsilon}} = \sqrt{\frac{1+\epsilon}{2}}\ket{00} + \sqrt{\frac{1-\epsilon}{2}},
-\end{equation}
-for some $\epsilon \in [0, 1]$.
+%------------------------------------------------------------------------------%
+\section{Quantum state cloning}
+\label{sec:qsc}
+%------------------------------------------------------------------------------%
 

### 2021-05-05 docs/paper/code/four_state_two_qubit_ppt.py

@@ -23,7 +23,7 @@ ensemble = Ensemble(
 ppt_min = OptDist(ensemble, "ppt", "min-error")
 ppt_min.solve()
 
-print(ppt_min.value)
+ppt_val = ppt_min.value
+ppt_closed_form = 1 / 2 * (1 + (n + m) / 2)
 
-print(1 / 2 * (1 + (n + m) / 2))
-
+assert np.isclose(ppt_val, ppt_closed_form)

### 2021-05-05 examples/opt_dist/positive/min_error/bell_states.py

@@ -17,21 +17,20 @@ from toqito.states import bell
 from qustop import State, Ensemble, OptDist
 
 dims = [2, 2]
-rho_1 = State(bell(0), dims)
-rho_2 = State(bell(1), dims)
-rho_3 = State(bell(2), dims)
-rho_4 = State(bell(3), dims)
+psi_0 = State(bell(0), dims)
+psi_1 = State(bell(1), dims)
+psi_2 = State(bell(2), dims)
+psi_3 = State(bell(3), dims)
 
-ensemble = Ensemble([rho_1, rho_2, rho_3, rho_4])
+ensemble = Ensemble([psi_0, psi_1, psi_2, psi_3])
 
 # Verify that states in the ensemble are mutually orthogonal:
 print(f"Are states mutually orthogonal: {ensemble.is_mutually_orthogonal}")
 
-sd = OptDist(
-    ensemble=ensemble, dist_measurement="pos", dist_method="min-error"
-)
+res = OptDist(ensemble, "pos", "min-error")
 
 # Mutually orthogonal states are optimally distinguishable--giving
 # an optimal value of one.
-sd.solve()
-print(sd.value)
+res.solve()
+# 1.0000000000879223
+print(res.value)

### 2021-05-05 examples/opt_dist/positive/min_error/three_nonorthogonal_states.py

@@ -16,28 +16,18 @@ import numpy as np
 
 from qustop import State, Ensemble, OptDist
 
-# Define single-qubit |0> and |1> basis states.
-e_0, e_1 = np.array([[1, 0]]).T, np.array([[0, 1]]).T
+# Define single-qubit |+> and |-> basis states.
 e_p, e_m = (
     1 / np.sqrt(2) * np.array([[1, 1]]).T,
     1 / np.sqrt(2) * np.array([[1, -1]]).T,
 )
 
-# rho_1 = 3/4 |+><+| + 1/4|-><-|
-rho_1 = 3 / 4 * (e_p * e_p.conj().T) + 1 / 4 * (e_m * e_m.conj().T)
-
-# rho_2 = 1/4 |+><+| + 3/4|-><-|
-rho_2 = 1 / 4 * (e_p * e_p.conj().T) + 3 / 4 * (e_m * e_m.conj().T)
-
-# rho_3 = 1/2 |+><+| + 1/2 |-><-|
-rho_3 = 1 / 2 * (e_p * e_p.conj().T) + 1 / 2 * (e_m * e_m.conj().T)
-
 dims = [2]
-rho_1 = State(rho_1, dims)
-rho_2 = State(rho_2, dims)
-rho_3 = State(rho_3, dims)
+phi_1 = State(np.sqrt(3 / 4) * e_p + np.sqrt(1 / 4) * e_m, dims)
+phi_2 = State(np.sqrt(1 / 4) * e_p + np.sqrt(3 / 4) * e_m, dims)
+phi_3 = State(np.sqrt(1 / 2) * e_p + np.sqrt(1 / 2) * e_m, dims)
 
-ensemble = Ensemble([rho_1, rho_2, rho_3])
+ensemble = Ensemble([phi_1, phi_2, phi_3])
 
 # Verify that ensemble consists of non-mutually-orthogonal states.:
 print(f"Is ensemble mutually orthogonal: {ensemble.is_mutually_orthogonal}")
@@ -45,10 +35,8 @@ print(f"Is ensemble mutually orthogonal: {ensemble.is_mutually_orthogonal}")
 # For any set of more than two states that are non-mutually orthogonal, no closed-form expression for optimal
 # distinguishability is known to exist. Therefore, we must resort to solving the SDP to determine what the optimal
 # probability is.
-sd = OptDist(
-    ensemble=ensemble, dist_measurement="pos", dist_method="min-error"
-)
[…]

### 2021-05-05 examples/opt_dist/positive/min_error/two_mixed_states.py

@@ -16,36 +16,29 @@ import numpy as np
 
 from qustop import State, Ensemble, OptDist
 
-# Define single-qubit |0> and |1> basis states.
-e_0, e_1 = np.array([[1, 0]]).T, np.array([[0, 1]]).T
+# Define single-qubit |+> and |-> basis states.
 e_p, e_m = (
     1 / np.sqrt(2) * np.array([[1, 1]]).T,
     1 / np.sqrt(2) * np.array([[1, -1]]).T,
 )
 
-# rho_1 = 3/4 |+><+| + 1/4|-><-|
-rho_1 = 3 / 4 * (e_p * e_p.conj().T) + 1 / 4 * (e_m * e_m.conj().T)
-
-# rho_2 = 1/4 |+><+| + 3/4|-><-|
-rho_2 = 1 / 4 * (e_p * e_p.conj().T) + 3 / 4 * (e_m * e_m.conj().T)
-
 dims = [2]
-rho_1 = State(rho_1, dims)
-rho_2 = State(rho_2, dims)
+# sqrt(3/4) |+> + sqrt(1/4)|->
+phi_1 = State(np.sqrt(3 / 4) * e_p + np.sqrt(1 / 4) * e_m, dims)
+# sqrt(1/4) |+> + sqrt(3/4)|->
+phi_2 = State(np.sqrt(1 / 4) * e_p + np.sqrt(3 / 4) * e_m, dims)
 
-# Verify that the states `rho_1` and `rho_2` are mixed:
-print(f"Is rho_1 pure: {rho_1.is_pure}")
-print(f"Is rho_2 pure: {rho_2.is_pure}")
+# Verify that the states `phi_1` and `phi_2` are mixed:
+print(f"Is phi_1 pure: {phi_1.is_pure}")
+print(f"Is phi_2 pure: {phi_2.is_pure}")
 
-ensemble = Ensemble([rho_1, rho_2])
+ensemble = Ensemble([phi_1, phi_2])
 
-sd = OptDist(
-    ensemble=ensemble, dist_measurement="pos", dist_method="min-error"
-)
+res = OptDist(ensemble, "pos", "min-error")
 
 # 0.7500000000609778
-sd.solve()
-print(sd.value)
+res.solve()
+print(res.value)
 
 # The closed-form equation yields: 3/4
-print(1 / 2 + 1 / 4 * np.linalg.norm(rho_1.value - rho_2.value, ord="nuc"))
[…]

### 2021-05-05 examples/opt_dist/positive/min_error/two_pure_states.py

@@ -16,34 +16,29 @@ import numpy as np
 
 from qustop import State, Ensemble, OptDist
 
-# Define single-qubit |0> and |1> basis states.
+# Define single-qubit |+> and |-> basis states.
 e_p, e_m = (
     1 / np.sqrt(2) * np.array([[1, 1]]).T,
     1 / np.sqrt(2) * np.array([[1, -1]]).T,
 )
 
-# Define v_1 = sqrt(3/4)|+> + sqrt(1/4)|->
-v_1 = np.sqrt(3 / 4) * e_p + np.sqrt(1 / 4) * e_m
-# Define v_2 = sqrt(1/4)|+> - sqrt(3/4)|->
-v_2 = np.sqrt(1 / 4) * e_p - np.sqrt(3 / 4) * e_m
-
 dims = [2]
-rho_1 = State(v_1, dims)
-rho_2 = State(v_2, dims)
+# sqrt(3/4)|+> + sqrt(1/4)|->
+psi_1 = State(np.sqrt(3 / 4) * e_p + np.sqrt(1 / 4) * e_m, dims)
+# sqrt(1/4)|+> - sqrt(3/4)|->
+psi_2 = State(np.sqrt(1 / 4) * e_p - np.sqrt(3 / 4) * e_m, dims)
 
-# Verify that the states `rho_1` and `rho_2` are pure:
-print(f"Is rho_1 pure: {rho_1.is_pure}")
-print(f"Is rho_2 pure: {rho_2.is_pure}")
+# Verify that the states `psi_1` and `psi_2` are pure:
+print(f"Is psi_1 pure: {psi_1.is_pure}")
+print(f"Is psi_2 pure: {psi_2.is_pure}")
 
-ensemble = Ensemble([rho_1, rho_2])
+ensemble = Ensemble([psi_1, psi_2])
 
-sd = OptDist(
-    ensemble=ensemble, dist_measurement="pos", dist_method="min-error"
-)
+res = OptDist(ensemble, "pos", "min-error")
 
 # 0.999999998061445
-sd.solve()
-print(sd.value)
+res.solve()
+print(res.value)
 
 # The closed-form equation yields: 0.9999999999999999 = 1
-print(1 / 2 + 1 / 4 * np.linalg.norm(rho_1.value - rho_2.value, ord="nuc"))
+print(1 / 2 + 1 / 4 * np.linalg.norm(psi_1.value - psi_2.value, ord="nuc"))

### 2021-05-05 examples/opt_dist/positive/unambiguous/three_nonorthogonal_states.py

@@ -16,32 +16,21 @@ import numpy as np
 
 from qustop import State, Ensemble, OptDist
 
-# Define single-qubit |0> and |1> basis states.
-e_0, e_1 = np.array([[1, 0]]).T, np.array([[0, 1]]).T
+# Define single-qubit |+> and |-> basis states.
 e_p, e_m = (
     1 / np.sqrt(2) * np.array([[1, 1]]).T,
     1 / np.sqrt(2) * np.array([[1, -1]]).T,
 )
 
-# rho_1 = 3/4 |+><+| + 1/4|-><-|
-rho_1 = 3 / 4 * (e_p * e_p.conj().T) + 1 / 4 * (e_m * e_m.conj().T)
-
-# rho_2 = 1/4 |+><+| + 3/4|-><-|
-rho_2 = 1 / 4 * (e_p * e_p.conj().T) + 3 / 4 * (e_m * e_m.conj().T)
-
-# rho_3 = 1/2 |+><+| + 1/2 |-><-|
-rho_3 = 1 / 2 * (e_p * e_p.conj().T) + 1 / 2 * (e_m * e_m.conj().T)
-
 dims = [2]
-rho_1 = State(rho_1, dims)
-rho_2 = State(rho_2, dims)
-rho_3 = State(rho_3, dims)
+phi_1 = State(np.sqrt(3 / 4) * e_p + np.sqrt(1 / 4) * e_m, dims)
+phi_2 = State(np.sqrt(1 / 4) * e_p + np.sqrt(3 / 4) * e_m, dims)
+phi_3 = State(np.sqrt(1 / 2) * e_p + np.sqrt(1 / 2) * e_m, dims)
 
-ensemble = Ensemble([rho_1, rho_2, rho_3])
-sd = OptDist(
-    ensemble=ensemble, dist_measurement="pos", dist_method="unambiguous"
-)
+ensemble = Ensemble([phi_1, phi_2, phi_3])
+
+res = OptDist(ensemble, "pos", "unambiguous")
 
 # Probability of distinguishing unambiguously is zero.
-sd.solve()
-print(sd.value)
+res.solve()
+print(res.value)

### 2021-05-05 examples/opt_dist/ppt/min_error/entanglement_cost_four_bell_states.py

@@ -43,6 +43,9 @@ sep_res.solve()
 
 eq = 1 / 2 * (1 + np.sqrt(1 - eps ** 2))
 
+# 0.9330127018922193
 print(eq)
+# 0.9330127016540999
 print(ppt_res.value)
+# 0.9330127016540999
 print(sep_res.value)

### 2021-05-05 examples/opt_dist/ppt/min_error/four_bell_states.py

@@ -19,14 +19,14 @@ from qustop import Ensemble, State, OptDist
 # Construct the corresponding density matrices of the Bell states.
 dims = [2, 2]
 states = [
-    State(bell(0) * bell(0).conj().T, dims),
-    State(bell(1) * bell(1).conj().T, dims),
-    State(bell(2) * bell(2).conj().T, dims),
-    State(bell(3) * bell(3).conj().T, dims),
+    State(bell(0), dims),
+    State(bell(1), dims),
+    State(bell(2), dims),
+    State(bell(3), dims),
 ]
-ensemble = Ensemble(states=states, probs=[1 / 4, 1 / 4, 1 / 4, 1 / 4])
-sd = OptDist(
-    ensemble=ensemble, dist_measurement="ppt", dist_method="min-error"
-)
-sd.solve()
-print(sd.value)
+ensemble = Ensemble(states, [1 / 4, 1 / 4, 1 / 4, 1 / 4])
+res = OptDist(ensemble, "ppt", "min-error")
+res.solve()
+
+# 0.5000000000530641
+print(res.value)

### 2021-05-05 examples/opt_dist/ppt/min_error/indstinguishable_mes.py

@@ -34,11 +34,10 @@ ensemble = Ensemble(
     ]
 )
 
-sd = OptDist(
-    ensemble=ensemble, dist_measurement="ppt", dist_method="min-error"
-)
-sd.solve()
-
 # The min-error probability of distinguishing via PPT
 # is equal to 7/8.
-print(sd.value)
+res = OptDist(ensemble, "ppt", "min-error")
+res.solve()
+
+# 0.87500000060847
+print(res.value)

### 2021-05-05 examples/opt_dist/ppt/min_error/werner_hiding_pair.py

@@ -30,13 +30,10 @@ ensemble = Ensemble(states)
 
 expected_val = 1 / 2 + 1 / (dim + 1)
 
-sd = OptDist(
-    ensemble=ensemble, dist_measurement="ppt", dist_method="min-error"
-)
-
-sd.solve()
+res = OptDist(ensemble, "ppt", "min-error")
+res.solve()
 
 # opt_ppt \approx 0.8333333333668715
-print(sd.value)
+print(res.value)
 # Closed-form expression is : 1/2 + 1/(dim+1) = 0.8333333333333333
 print(expected_val)

### 2021-05-05 examples/opt_dist/ppt/unambiguous/indstinguishable_mes.py

@@ -34,11 +34,10 @@ ensemble = Ensemble(
     ]
 )
 
-sd = OptDist(
-    ensemble=ensemble, dist_measurement="ppt", dist_method="unambiguous"
-)
-sd.solve()
-
 # The unambiguous probability of distinguishing via PPT
 # is equal to 3/4.
+res = OptDist(ensemble, "ppt", "unambiguous")
+res.solve()
+
+# 0.7499999975754753
 print(sd.value)

### 2021-05-05 examples/opt_dist/sep/min_error/entanglement_cost_three_bell_states.py

@@ -40,5 +40,8 @@ sep_res.solve()
 
 eq = 1 / 3 * (2 + np.sqrt(1 - eps ** 2))
 
+# 0.9553418012614794
 print(eq)
+
+# 0.9583970406126399
 print(sep_res.value)

### 2021-05-05 examples/opt_dist/sep/min_error/feng_upb.py

@@ -30,27 +30,14 @@ phi_8 = np.kron((e_0 - e_1 + e_2), (e_1 + e_2 + e_3) / 3)
 
 dims = [4, 4]
 states = [
-    State(phi_1 * phi_1.conj().T, dims),
-    State(phi_2 * phi_2.conj().T, dims),
-    State(phi_3 * phi_3.conj().T, dims),
-    State(phi_4 * phi_4.conj().T, dims),
-    State(phi_5 * phi_5.conj().T, dims),
-    State(phi_6 * phi_6.conj().T, dims),
-    State(phi_7 * phi_7.conj().T, dims),
-    State(phi_8 * phi_8.conj().T, dims),
+    State(phi_1, dims), State(phi_2, dims),
+    State(phi_3, dims), State(phi_4, dims),
+    State(phi_5, dims), State(phi_6, dims),
+    State(phi_7, dims), State(phi_8, dims),
 ]
 ensemble = Ensemble(states=states)
-sd = OptDist(
-    ensemble,
-    "sep",
-    "min-error",
-    return_optimal_meas=True,
-    solver="SCS",
-    verbose=True,
-    eps=1e-4,
-    level=2,
-)
-sd.solve()
+res = OptDist(ensemble, "sep", "min-error", level=2)
+res.solve()
 
 # 0.9967296337698935
-print(sd.value)
+print(res.value)

### 2021-05-05 examples/opt_dist/sep/min_error/indistinguishable_mes.py

@@ -20,29 +20,22 @@ from qustop import State, Ensemble, OptDist
 
 # Define the maximally entangled states from arXiv1107.3224
 dims = [2, 2, 2, 2]
-rho_0 = np.kron(bell(0), bell(0)) * np.kron(bell(0), bell(0)).conj().T
-rho_1 = np.kron(bell(2), bell(1)) * np.kron(bell(2), bell(1)).conj().T
-rho_2 = np.kron(bell(3), bell(1)) * np.kron(bell(3), bell(1)).conj().T
-rho_3 = np.kron(bell(1), bell(1)) * np.kron(bell(1), bell(1)).conj().T
-
 ensemble = Ensemble(
     [
-        State(rho_0, dims),
-        State(rho_1, dims),
-        State(rho_2, dims),
-        State(rho_3, dims),
+        State(np.kron(bell(0), bell(0)), dims),
+        State(np.kron(bell(2), bell(1)), dims),
+        State(np.kron(bell(3), bell(1)), dims),
+        State(np.kron(bell(1), bell(1)), dims),
     ]
 )
 ensemble.swap([2, 3])
 
-res = OptDist(ensemble,
-              "sep",
-              "min-error",
-              return_optimal_meas=True,
-              solver="SCS",
-              verbose=True,
-              eps=1e-6,
-              level=2)
+res = OptDist(
+    ensemble,
+    "sep",
+    "min-error",
+    level=2,
+)
 res.solve()
 
 # The min-error probability of distinguishing via

### 2021-05-05 examples/opt_dist/sep/min_error/tile_upb.py

@@ -17,7 +17,7 @@ from toqito.states import basis, tile
 from qustop import Ensemble, State, OptDist
 
 
-# Construct the corresponding density matrices of the Bell states.
+# Construct the corresponding density matrices of the Tiles UPB.
 dims = [3, 3]
 states = [
     State(tile(0) * tile(0).conj().T, dims),
@@ -26,18 +26,9 @@ states = [
     State(tile(3) * tile(3).conj().T, dims),
     State(tile(4) * tile(4).conj().T, dims),
 ]
-ensemble = Ensemble(states=states)
-sd = OptDist(
-    ensemble,
-    "sep",
-    "min-error",
-    return_optimal_meas=True,
-    solver="SCS",
-    verbose=False,
-    eps=1e-6,
-    level=2,
-)
-sd.solve()
+ensemble = Ensemble(states)
+res = OptDist(ensemble, "sep", "min-error", level=2)
+res.solve()
 
 # 0.999999
-print(sd.value)
+print(res.value)

### 2021-05-05 examples/opt_dist/sep/min_error/tile_upb_plus_pure.py

@@ -18,19 +18,13 @@ from toqito.states import basis, tile
 from qustop import Ensemble, State, OptDist
 
 
-# Construct the corresponding density matrices of the Bell states.
 dims = [3, 3]
 e_0, e_1, e_2 = basis(3, 0), basis(3, 1), basis(3, 2)
-psi = (
-    1
-    / 2
-    * (
-        np.kron(e_0, e_0)
-        + np.kron(e_0, e_1)
-        - np.kron(e_0, e_2)
-        - np.kron(e_1, e_2)
-    )
-)
+
+# Define a pure state to add to the ensemble.
+psi = 1 / 2 * (np.kron(e_0, e_0) + np.kron(e_0, e_1) - np.kron(e_0, e_2) - np.kron(e_1, e_2))
+
+# Construct the corresponding density matrices of the Tiles UPB + pure state:
 states = [
     State(tile(0) * tile(0).conj().T, dims),
     State(tile(1) * tile(1).conj().T, dims),
@@ -39,18 +33,10 @@ states = [
     State(tile(4) * tile(4).conj().T, dims),
     State(psi * psi.conj().T, dims),
 ]
-ensemble = Ensemble(states=states)
-sd = OptDist(
-    ensemble,
-    "sep",
-    "min-error",
-    return_optimal_meas=True,
-    solver="SCS",
-    verbose=False,
-    eps=1e-6,
-    level=2,
-)
-sd.solve()
+ensemble = Ensemble(states)
+
+res = OptDist(ensemble, "sep", "min-error", level=2)
+res.solve()
 
 # 0.9860588510298623
-print(sd.value)
+print(res.value)

### 2021-05-05 qustop/opt_dist/opt_dist.py

@@ -76,18 +76,28 @@ class OptDist:
         if len(self.ensemble) == 2:
             # If the states are mutually orthogonal and both pure states, they are perfectly distinguishable
             # arXiv:0007098.
-            if self.ensemble.is_mutually_orthogonal and self.ensemble[0].is_pure and self.ensemble[1].is_pure:
+            if (
+                self.ensemble.is_mutually_orthogonal
+                and self.ensemble[0].is_pure
+                and self.ensemble[1].is_pure
+            ):
                 return 1.0
 
             # In any case, there is a closed-form expression for the distinguishability of two density matrices.
             # TODO:
             else:
-                return 1/2 + trace_norm(self.ensemble.probs[0] * self.ensemble.density_matrices[0] -
-                                        self.ensemble.probs[1] * self.ensemble.density_matrices[1])
+                return 1 / 2 + trace_norm(
+                    self.ensemble.probs[0] * self.ensemble.density_matrices[0]
+                    - self.ensemble.probs[1]
+                    * self.ensemble.density_matrices[1]
+                )
 
         if len(self.ensemble) == 3:
             # Check if ensemble is in :math:`\mathbb{C}^2 \otimes \mathbb{C}^2`:
-            if len(self.ensemble.dims) == 2 and self.ensemble.dims[0] == self.ensemble.dims == 2:
+            if (
+                len(self.ensemble.dims) == 2
+                and self.ensemble.dims[0] == self.ensemble.dims == 2
+            ):
                 # If two out of the three states are product states and all three states are pure then according to
                 # arXiv:0202034, the states are perfectly distinguishable.
                 # TODO
@@ -98,7 +108,10 @@ class OptDist:
             # If ensemble is in :math:`\mathbb{C}^2 \otimes \mathbb{C}^2` and all states are product states, the
             # ensemble is perfectly distinguishable according to arXiv:0202034
             # TODO
-            if len(self.ensemble.dims) == 2 and self.ensemble.dims[0] == self.ensemble.dims == 2:
+            if (
+                len(self.ensemble.dims) == 2
+                and self.ensemble.dims[0] == self.ensemble.dims == 2
+            ):
                 pass
             pass
 

### 2021-05-05 qustop/opt_dist/positive.py

@@ -146,11 +146,14 @@ class Positive:
                 for i, _ in enumerate(self._states):
                     if i != j:
                         sum_val += (
-                            cvxpy.real(scalar_vars[i][j])
+                            scalar_vars[i][j]
                             * self._probs[i]
                             * self._states[i]
                         )
-                constraints.append(y_var - self._probs[j] * self._states[j] + sum_val >> 0)
+                constraints.append(
+                    y_var - self._probs[j] * self._states[j] + sum_val >> 0
+                )
+            constraints.append(y_var >> 0)
 
         objective = cvxpy.Minimize(cvxpy.trace(cvxpy.real(y_var)))
         problem = cvxpy.Problem(objective, constraints)

### 2021-05-05 qustop/opt_dist/ppt.py

@@ -114,14 +114,15 @@ class PPT:
 
         # Valid collection of measurements need to sum to the identity
         # operator.
-        constraints.append(cvxpy.sum(meas) == np.identity(self._ensemble.shape[0]))
+        constraints.append(
+            cvxpy.sum(meas) == np.identity(self._ensemble.shape[0])
+        )
 
         # Construct the objective function by taking the inner product of each of the states with
         # each of the measurement variables scaled by the corresponding probability of the given
         # state being selected by the ensemble.
         obj_func = [
-            self._probs[i]
-            * cvxpy.trace(self._states[i].conj().T @ meas[i])
+            self._probs[i] * cvxpy.trace(self._states[i].conj().T @ meas[i])
             for i, _ in enumerate(self._states)
         ]
         obj_sum = cvxpy.sum(obj_func)
@@ -152,7 +153,8 @@ class PPT:
                 for _ in range(num_measurements)
             ]
             constraints = [
-                y_var - self._probs[i] * self._states[i] >> partial_transpose(dual_vars[i], self._sys, self._dims)
+                y_var - self._probs[i] * self._states[i]
+                >> partial_transpose(dual_vars[i], self._sys, self._dims)
                 for i in range(num_measurements)
             ]
             for i in range(num_measurements):
@@ -180,8 +182,14 @@ class PPT:
                             * self._probs[i]
                             * self._states[i]
                         )
-                constraints.append(y_var - self._probs[j] * self._states[j] + sum_val >> partial_transpose(dual_vars[j], self._sys, self._dims))
-            constraints.append(y_var >> partial_transpose(dual_vars[-1], self._sys, self._dims))
+                constraints.append(
+                    y_var - self._probs[j] * self._states[j] + sum_val
+                    >> partial_transpose(dual_vars[j], self._sys, self._dims)
+                )
+            constraints.append(
+                y_var
+                >> partial_transpose(dual_vars[-1], self._sys, self._dims)
+            )
 
         objective = cvxpy.Minimize(cvxpy.trace(cvxpy.real(y_var)))
         problem = cvxpy.Problem(objective, constraints)

### 2021-05-05 qustop/opt_dist/separable.py

@@ -73,7 +73,9 @@ class Separable:
         self._sym_ext_dim_list = [self._dims[0]] * (self._level + 1)
 
         # dim(X_1) * dim(Y_1) * dim(Y_2) * ... * dim(Y_{level})
-        self._sym_ext_dims = self._ensemble.shape[0] * np.prod(self._sym_ext_dim_list)
+        self._sym_ext_dims = self._ensemble.shape[0] * np.prod(
+            self._sym_ext_dim_list
+        )
 
     def solve(self) -> Union[float, Tuple[float, List[cvxpy.Variable]]]:
         """Solve either the primal or dual problem for the separable SDP."""
@@ -105,15 +107,15 @@ class Separable:
             for i, _ in enumerate(self._states)
         ]
         obj_func = [
-            self._probs[i]
-            * cvxpy.trace(self._states[i].conj().T @ meas[i])
+            self._probs[i] * cvxpy.trace(self._states[i].conj().T @ meas[i])
             for i, _ in enumerate(self._states)
         ]
 
         for k, _ in enumerate(self._states):
             # Tr_{Y_2 \otimes ... \otimes Y_l}(X_k) = meas[k]:
             constraints.append(
-                partial_trace(x_var[k], self._sym_ext_sys_list, dim_list) == meas[k]
+                partial_trace(x_var[k], self._sym_ext_sys_list, dim_list)
+                == meas[k]
             )
             # (I_X \otimes Pi) X_k (I_X \otimes Pi) = X_k
             # where "Pi" is the symmetric projection on (Y \ovee Y_2 \ovee ... \ovee Y_l)
@@ -131,7 +133,9 @@ class Separable:
             constraints.append(meas[k] >> 0)
             constraints.append(x_var[k] >> 0)
 
-        constraints.append(cvxpy.sum(meas) == np.identity(self._ensemble.shape[0]))
+        constraints.append(
+            cvxpy.sum(meas) == np.identity(self._ensemble.shape[0])
+        )
 
         obj_sum = cvxpy.sum(obj_func)
         objective = cvxpy.Maximize(cvxpy.real(obj_sum))

### 2021-05-05 qustop/opt_dist/tests/test_positive.py

@@ -112,10 +112,12 @@ def test_unambiguous_state_distinguishability_two_states():
     primal_res.solve()
     np.testing.assert_equal(np.isclose(primal_res.value, 1), True)
 
-    dual_res = OptDist(ensemble=ensemble,
-                       dist_measurement="pos",
-                       dist_method="unambiguous",
-                       return_optimal_meas=False)
+    dual_res = OptDist(
+        ensemble=ensemble,
+        dist_measurement="pos",
+        dist_method="unambiguous",
+        return_optimal_meas=False,
+    )
     dual_res.solve()
     np.testing.assert_equal(np.isclose(dual_res.value, 1), True)
 
@@ -144,13 +146,17 @@ def test_state_distinguishability_two_mixed_states():
         ensemble=ensemble, dist_measurement="pos", dist_method="min-error"
     )
     primal_res.solve()
-    np.testing.assert_equal(np.isclose(primal_res.value, 3 / 4, atol=0.001), True)
+    np.testing.assert_equal(
+        np.isclose(primal_res.value, 3 / 4, atol=0.001), True
+    )
 
     dual_res = OptDist(
         ensemble=ensemble, dist_measurement="pos", dist_method="min-error"
     )
     dual_res.solve()
-    np.testing.assert_equal(np.isclose(dual_res.value, 3 / 4, atol=0.001), True)
+    np.testing.assert_equal(
+        np.isclose(dual_res.value, 3 / 4, atol=0.001), True
+    )
 
 
 def test_state_distinguishability_three_non_orthogonal_states():
@@ -182,24 +188,39 @@ def test_state_distinguishability_three_non_orthogonal_states():
 
     # Primal min-error:
     primal_min_error_res = OptDist(
-        ensemble=ensemble, dist_measurement="pos", dist_method="min-error", return_optimal_meas=True
+        ensemble=ensemble,
+        dist_measurement="pos",
+        dist_method="min-error",
+        return_optimal_meas=True,
     )
     primal_min_error_res.solve()
-    np.testing.assert_equal(np.isclose(primal_min_error_res.value, 1/2, atol=0.001), True)
+    np.testing.assert_equal(
+        np.isclose(primal_min_error_res.value, 1 / 2, atol=0.001), True
+    )
 
     # Dual min-error:
     dual_min_error_res = OptDist(
[…]

### 2021-05-05 qustop/opt_dist/tests/test_ppt.py

@@ -394,33 +394,52 @@ def test_ppt_five_mes_generalized_bell():
     n = 5
     dims = [5, 5]
 
-    rho_1 = State(1 / n * (vec(gen_pauli(0, 0, n)) @ vec(gen_pauli(0, 0, n)).conj().T), dims)
-    rho_2 = State(1 / n * (vec(gen_pauli(1, 1, n)) @ vec(gen_pauli(1, 1, n)).conj().T), dims)
-    rho_3 = State(1 / n * (vec(gen_pauli(1, 2, n)) @ vec(gen_pauli(1, 2, n)).conj().T), dims)
-    rho_4 = State(1 / n * (vec(gen_pauli(3, 1, n)) @ vec(gen_pauli(3, 1, n)).conj().T), dims)
-    rho_5 = State(1 / n * (vec(gen_pauli(3, 2, n)) @ vec(gen_pauli(3, 2, n)).conj().T), dims)
+    rho_1 = State(
+        1 / n * (vec(gen_pauli(0, 0, n)) @ vec(gen_pauli(0, 0, n)).conj().T),
+        dims,
+    )
+    rho_2 = State(
+        1 / n * (vec(gen_pauli(1, 1, n)) @ vec(gen_pauli(1, 1, n)).conj().T),
+        dims,
+    )
+    rho_3 = State(
+        1 / n * (vec(gen_pauli(1, 2, n)) @ vec(gen_pauli(1, 2, n)).conj().T),
+        dims,
+    )
+    rho_4 = State(
+        1 / n * (vec(gen_pauli(3, 1, n)) @ vec(gen_pauli(3, 1, n)).conj().T),
+        dims,
+    )
+    rho_5 = State(
+        1 / n * (vec(gen_pauli(3, 2, n)) @ vec(gen_pauli(3, 2, n)).conj().T),
+        dims,
+    )
 
     ensemble = Ensemble([rho_1, rho_2, rho_3, rho_4, rho_5])
 
-    primal_res = OptDist(ensemble,
-                         "ppt",
-                         "min-error",
-                         return_optimal_meas=True,
-                         solver="SCS",
-                         verbose=False,
-                         eps=1e-6)
+    primal_res = OptDist(
+        ensemble,
+        "ppt",
+        "min-error",
+        return_optimal_meas=True,
+        solver="SCS",
+        verbose=False,
+        eps=1e-6,
+    )
     primal_res.solve()
     np.testing.assert_equal(
[…]

### 2021-05-05 qustop/opt_dist/tests/test_separable.py

@@ -108,28 +108,32 @@ def test_symmetric_extension_hierarchy_ydy_states():
     )
     ensemble.swap([2, 3])
 
-    primal_res = OptDist(ensemble,
-                         "sep",
-                         "min-error",
-                         return_optimal_meas=True,
-                         solver="SCS",
-                         verbose=False,
-                         eps=1e-6,
-                         level=2)
+    primal_res = OptDist(
+        ensemble,
+        "sep",
+        "min-error",
+        return_optimal_meas=True,
+        solver="SCS",
+        verbose=False,
+        eps=1e-6,
+        level=2,
+    )
     primal_res.solve()
 
     # The min-error probability of distinguishing via
     # separable measurements is equal to 3/4.
     np.testing.assert_equal(np.isclose(primal_res.value, 3 / 4), True)
 
-    dual_res = OptDist(ensemble,
-                       "sep",
-                       "min-error",
-                       return_optimal_meas=True,
-                       solver="SCS",
-                       verbose=False,
-                       eps=1e-6,
-                       level=2)
+    dual_res = OptDist(
+        ensemble,
+        "sep",
+        "min-error",
+        return_optimal_meas=True,
+        solver="SCS",
+        verbose=False,
+        eps=1e-6,
+        level=2,
+    )
     dual_res.solve()
 
     # The min-error probability of distinguishing via
